### 2024-02-12 outputs/paper/paper.qmd
update folder

---
title: "Grade Distribution Among Genders"
subtitle: "My subtitle if needed"
author: 
  - Faiza Imam 
  - Quang Mai 
  - Catherine Punnoose 
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

# Load packages
library(readstata13)
library(readr)
library(knitr)
library(kableExtra)
library(tidyverse)
library(janitor)

# Load data
# inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
std_data <- read_csv(here::here("inputs/data/stdsurvey.csv"))
# exp_data <- read.csv(here::here("inputs/data/experiment.csv"))
```

# TESTING GRAPHS

Our data (@tbl-studentgender).

```{r}
#| label: tbl-studentgender
#| tbl-cap: "Number of students enrolled in class, by gender"
#| warning: false
#| message: false
#| echo: false

std_data |>
  count(std_female) %>% 
  kable(
    col.names = c("Gender", "Number of students")
  )
```

# Introduction

<intro>

# Data {#sec-data}

<data>

# Model
<model>

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

\newpage

# References

### 2024-02-12 testing_graphs.qmd
update folder

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
---

```{r}
#| include: false
#| warning: false
#| message: false

#loading packages
library(readstata13)
library(readr)

#reading in the stata file
instsurvey <- read.dta13(here::here("inputs/data/instsurvey.dta"))
stdsurvey <- read.dta13(here::here("inputs/data/stdsurvey.dta"))
experiment <- read.dta13(here::here("inputs/data/experiment.dta"))

#writing to csv
write_csv(instsurvey, here::here("inputs/data/instsurvey.csv"))
write_csv(stdsurvey, here::here("inputs/data/stdsurvey.csv"))
write_csv(experiment, here::here("inputs/data/experiment.csv"))

```

# TESTING GRAPHS
```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(janitor)

# inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
std_data <- read.csv(here::here("inputs/data/stdsurvey.csv"))
# exp_data <- read.csv(here::here("inputs/data/experiment.csv"))

std_data |>
  count(std_standing)

```

```{r}
#| include: false
#| warning: false
#| message: false

# Install and load necessary packages
install.packages("knitr")
install.packages("kableExtra")
library(knitr)
library(kableExtra)

# Create a data frame with the given values
data <- data.frame(
  Category = c("Percent of records", "Grade change", "Positive grade change", 
               "Negative grade change", "Female instructor", "Days between grade changes", 
               "GPA", "Percent in College of Agriculture", "College of Business", 
               "College of Engineering", "College of Human Sciences", 
               "College of Liberal Arts", "College of Natural Resources", 
               "College of Natural Sciences", "College of Veterinary Sciences", 
               "Intra-university", "Observations"),
  All = c(100, 0.464, 0.439, 0.025, 44.9, 25.8, 3.04, 4.5, 10.8, 4.8, 
          12.6, 32.2, 4.6, 23.3, 3.4, 3.9, 1341552),
  Female = c(53.4, 0.424, 0.404, 0.021, 50.0, 24.9, 3.13, 4.9, 8.6, 1.9, 
              15.5, 33.6, 3.5, 23.2, 4.4, 4.4, 716772),
  Male = c(46.6, 0.509, 0.479, 0.031, 38.9, 26.7, 2.94, 4.0, 13.2, 8.2, 
            9.1, 30.6, 5.9, 23.4, 2.3, 3.3, 624780)
)

# Create a kable table
tbl <- kable(data, format = "html", align = "c") %>%
  kable_styling()

# Print the table
print(tbl)

```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows.

# Data {#sec-data}

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

\newpage

# References

### 2024-02-12 scripts/00-simulate_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
+# Purpose: Simulates 
 # Author: Rohan Alexander [...UPDATE THIS...]
 # Date: 11 February 2023 [...UPDATE THIS...]
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]

### 2024-02-12 scripts/01-download_data.R

@@ -2,7 +2,7 @@
 # Purpose: Downloads and saves survey data to new file
 # Author: Faiza Imam, Catherine Punnoose, Quang Mai 
 # Data: survey.dta
-# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
+# Contact: 
 # License: MIT
 # Pre-requisites: Have downloaded survey.dta from https://doi.org/10.7910/DVN/QXJDJ5
 

### 2024-02-12 scripts/02-data_cleaning.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Catherine Punnoose, Quang Mai, Faiza Imam 
+# Date: 13 Feb 2024 
+# Contact: catherine.punnoose@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
@@ -10,35 +10,30 @@
 #### Workspace setup ####
 library(tidyverse)
 
-#### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
-
-cleaned_data <-
-  raw_data |>
+### CLEANING DATA ###
+### Cleaning Instructor	Survey	Data (instsurvey) ###
+inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
+inst_data_cleaned <- 
+  inst_data |>
   janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
+  select(pctrequests_fn) |>
   tidyr::drop_na()
 
-#### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+
[…]

### 2024-02-12 scripts/03-test_data.R

@@ -1,15 +1,80 @@
+#### Test data ####
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests cleaned datasets 
+# Author: Quang Mai, Catherine Punnoose and Faiza Imam
+# Date: 11 February 2024
+# Contact:
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: reload 01-download_data.R and 02-data_cleaning.R
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(dplyr)
+library(janitor)
+
+
+#### Read in cleaned data ####
+
+# read cleaned data on arrests and strip searches
+std_data_cleaned = read_csv(
+  file = here("outputs/data/std_data_cleaned.csv"),
+  show_col_types = FALSE
+)
+
+# read cleaned data on race and gender and strip searches
+inst_data_cleaned = read_csv(
+  file = here("outputs/data/inst_data_cleaned.csv"),
+  show_col_types = FALSE
+)
+
 
 #### Test data ####
+
+
+
+# Test 1: check that there are  0 minimum maledown/femaledown in inst_data_cleaned
+inst_data_cleaned$maledown_fn |> min() == 0
+inst_data_cleaned$femaledown_fn |> min() == 0
+
+
+
+# Test 2: check that the std dataset's num_class variable and see if it has minium 0 class and maximum 5 classes
+std_data_cleaned$num_class |> min() == 0
+std_data_cleaned$num_class |> max() == 5
+
+
+
+# Test 3: check that the std dataset's consider_regrade variable has three unique datanames only 
+std_data_cleaned$consider_regrade |> unique() |> length() == 3
+
+
+
+# Test 4: check that there are exactly 1295 observations in the std dataset without NA as its datapoints
+std_data_cleaned$participantcode|> unique() |> length() == 1295
+
+
+
+# Test 5: check that there are exactly 2 options of "1" and "0" for gender in the std dataset using the std_male variable
+std_data_cleaned$std_male |> unique() |> length() == 2
+
+
+
[…]

### 2024-02-12 outputs/paper/paper.qmd
clean up folder

@@
 library(janitor)
+library(dplyr)
 
 # Load data
-# inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
+inst_data <- read.csv(here::here("outputs/data/inst_data_cleaned.csv"))
+
 std_data <- read_csv(here::here("inputs/data/stdsurvey.csv"))
+
 # exp_data <- read.csv(here::here("inputs/data/experiment.csv"))
@@
 
-# TESTING GRAPHS
+# FIGURE 3
 
-Our data (@tbl-studentgender).
+Our data (@tbl-figure3).
 
 ```{r}
-#| label: tbl-studentgender
-#| tbl-cap: "Number of students enrolled in class, by gender"
+#| label: tbl-figure3
+#| tbl-cap: "Instructor Survey: Regrade Results by Timing and Students’ Gender"
 #| warning: false
@@
 
-std_data |>
-  count(std_female) %>% 
+#Code Assisted from Chat GPT 3.5
+# End of Semester Results MALE
+
+male_dta <- inst_data |>
+              select(maleup_fn, malesame_fn, maledown_fn)
+
+maleup_avg <- mean(male_dta$maleup_fn, na.rm = TRUE)
+malesame_avg <- mean(male_dta$malesame_fn, na.rm = TRUE)
+maledown_avg <- mean(male_dta$maledown_fn, na.rm = TRUE)
+
+males <- data.frame(
+  value = c(maleup_avg, malesame_avg, maledown_avg),
+  category = c("Grade Increase", "No Change", "Grade Decrease")
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'category' variable to a factor with the specified order
+males$category <- factor(males$category, levels = category_order)
+
+# Set custom breaks for the y-axis
+custom_breaks <- seq(0, 90, by = 30)
+
+# Create a bar graph using ggplot
+ggplot(males, aes(x = category, y = value, fill = category)) + ylim(0, 90) +
+  geom_bar(stat = "identity") +
+  geom_text(aes(label = round(value)), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(title = "Panel A. End of semester, male students",
+       x = "Category",
+       y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
+  scale_y_continuous(breaks = custom_breaks) +  # Set custom breaks for y-axis
+  theme_minimal()
+
+# End of Semester Results FEMALE
+
+female_dta <- inst_data |>
+              select(femaleup_fn, femalesame_fn, femaledown_fn)
+
+femaleup_avg <- mean(female_dta$femaleup_fn, na.rm = TRUE)
+femalesame_avg <- mean(female_dta$femalesame_fn, na.rm = TRUE)
+femaledown_avg <- mean(female_dta$femaledown_fn, na.rm = TRUE)
+
+females <- data.frame(
+  value = c(femaleup_avg, femalesame_avg, femaledown_avg),
+  category = c("Grade Increase", "No Change", "Grade Decrease")
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'category' variable to a factor with the specified order
+females$category <- factor(females$category, levels = category_order)
+
+# Set custom breaks for the y-axis
+custom_breaks <- seq(0, 90, by = 30)
+
+# Create a bar graph using ggplot
+ggplot(females, aes(x = category, y = value, fill = category)) + ylim(0, 90) +
+  geom_bar(stat = "identity") +
+  geom_text(aes(label = round(value)), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(title = "Panel A. End of semester, female students",
+       x = "Category",
+       y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
+  scale_y_continuous(breaks = custom_breaks) +  # Set custom breaks for y-axis
+  theme_minimal()
+
+```
+
+# FIGURE 2
+
+Figure 2. Student Survey: Number of Classes Students Considered for Regrade Requests by Students’ Gender
+
+```{r}
+classes_dta <- std_data |>
+              select(std_male, num_class, consider_regrade)|>
+              rename(Gender = std_male) |>
+              filter(is.na(consider_regrade) | consider_regrade != "No")
+
+classes_dta <- classes_dta |>
+  group_by(num_class, Gender, consider_regrade) |>
+  count() |>
+  group_by(Gender, consider_regrade) |>
+  mutate(Percentage = round(n/sum(n)*100, 1))|>
+  mutate(num_class = case_match(num_class, 
+                             0 ~ "0 class",
+                             1 ~ "1 class",
+                             2 ~ "2 classes",
+                             3 ~ "3 classes",
+                             4 ~ "4 classes",
+                             5 ~ "5 classes"))
+
+classes_dta$consider_regrade[classes_dta$consider_regrade == "Yes"] <- "No"
+classes_dta$consider_regrade[is.na(classes_dta$consider_regrade)] <- "Yes"
+classes_dta$Gender[classes_dta$Gender == "1"] <- "Male"
+classes_dta$Gender[classes_dta$Gender == "0"] <- "Female"
+
+classes_dta |>
+  filter(consider_regrade != "No") |>
+  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)
+
+head(classes_dta, 10) |>
   kable(
-    col.names = c("Gender", "Number of students")
+    col.names = c("Number of Classes", "Gender", "Consider Regrade", "Count", "Percentage"),
+    booktabs = TRUE,
+    align = c("c", "c", "c", "c", "c")
   )
+
+classes_dta |>
+ggplot(aes(x = num_class, y = Percentage, fill = Gender)) + 
+  geom_bar(stat="identity", position = "dodge") +
+  theme_minimal() +
+  theme(legend.key.size = unit(0.5, 'cm')) +
+  geom_text(aes(label=Percentage), position=position_dodge(width=0.9), vjust=-0.25) +
+  labs(x = "Classes",
+       y = "Distribution by gender (percent)") +
+  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +
+  scale_x_discrete(labels = c("0 class", "1 class", "2 classes", "3 classes", "4 classes", "5+ classes"))
+
 ```

### 2024-02-12 scripts/02-data_cleaning.R

@@ -8,27 +8,36 @@
 # Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
+library(dplyr)
+library(tidyr)
+library(janitor)
 library(tidyverse)
 
 ### CLEANING DATA ###
 ### Cleaning Instructor	Survey	Data (instsurvey) ###
-inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
+# Read data
+#inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
+
+inst_data <- read.csv("inputs/data/instsurvey.csv")
+
 inst_data_cleaned <- 
   inst_data |>
   janitor::clean_names() |>
-  select(pctrequests_fn) |>
+  select(id, maleup_fn, femaleup_fn, malesame_fn, femalesame_fn, maledown_fn, femaledown_fn) |>
   tidyr::drop_na()
 
+write_csv(inst_data_cleaned, "outputs/data/inst_data_cleaned.csv")
 
 ### Cleaning Stdsurvey ###
-std_data <- read.csv(here::here("inputs/data/stdsurvey.csv"))
+std_data <- read.csv("inputs/data/stdsurvey.csv")
 
 std_data_cleaned <- 
   std_data |>
   janitor::clean_names() |>
-  select(std_female, std_standing, std_male, consider_regrade, everasked, num_class, num_asked) |>
-  tidyr::drop_na()
-  
+  select(participantcode, std_female, std_standing, std_male, consider_regrade, everasked, num_class, num_asked)
+
+
+
 #### Save Clean Stdsurvey data ####
 write_csv(std_data_cleaned, "outputs/data/std_data_cleaned.csv")
 

### 2024-02-12 outputs/paper/paper.qmd
update readme

@@
   rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)
-
 head(classes_dta, 10) |>
@@
 classes_dta |>
+filter(consider_regrade != "No") |>
 ggplot(aes(x = num_class, y = Percentage, fill = Gender)) + 

### 2024-02-12 scripts/02-data_cleaning.R
refine folder

@@ -26,7 +26,7 @@ inst_data_cleaned <-
   select(id, maleup_fn, femaleup_fn, malesame_fn, femalesame_fn, maledown_fn, femaledown_fn) |>
   tidyr::drop_na()
 
-write_csv(inst_data_cleaned, "outputs/data/inst_data_cleaned.csv")
+write_csv(inst_data_cleaned, "inputs/data/inst_data_cleaned.csv")
 
 ### Cleaning Stdsurvey ###
 std_data <- read.csv("inputs/data/stdsurvey.csv")
@@ -39,7 +39,7 @@ std_data_cleaned <-
 
 
 #### Save Clean Stdsurvey data ####
-write_csv(std_data_cleaned, "outputs/data/std_data_cleaned.csv")
+write_csv(std_data_cleaned, "inputs/data/std_data_cleaned.csv")
 
 ### Cleaning Experiment ###
 #exp_data <- read.csv(here::here("inputs/data/experiment.csv"))

### 2024-02-12 scripts/03-test_data.R

@@ -17,13 +17,13 @@ library(janitor)
 
 # read cleaned data on arrests and strip searches
 std_data_cleaned = read_csv(
-  file = here("outputs/data/std_data_cleaned.csv"),
+  file = here("inputs/data/std_data_cleaned.csv"),
   show_col_types = FALSE
 )
 
 # read cleaned data on race and gender and strip searches
 inst_data_cleaned = read_csv(
-  file = here("outputs/data/inst_data_cleaned.csv"),
+  file = here("inputs/data/inst_data_cleaned.csv"),
   show_col_types = FALSE
 )
 

### 2024-02-14 outputs/paper/paper.qmd
refine folder
update paper

@@
 ---
-title: "Grade Distribution Among Genders"
-subtitle: "My subtitle if needed"
-author: 
-  - Faiza Imam 
-  - Quang Mai 
-  - Catherine Punnoose 
-thanks: "Code and data are available at: LINK."
+title: "The Relationship Between Gender Identities and Regrades among Undergraduate Students, 2010-2016"
+subtitle: "A replication of Li and Zahar;"
+author: Faiza Imam, Quang Mai & Catherine Punnoose 
+thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git"
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Academia is a complex ecosystem that feeds off a network of social, cultural and innovative influences which often, stem beyond societal norms.
+This paper replicates the gender implications regarding results in college students and explores potential fluctuations in request patterns over a semester by specifically analyzing the number of classes taken by students and their willingness to submit a grade request throughout the semester.
+Our results show that there is a trend for female students to submit regrade requests while taking fewer courses compared to a higher course load.
+Female students experienced grade increases (3%) compared to their male counterparts.
+We call for further investigation around this topic to understand gender disparities within the world of academia.
+"
 format: pdf
+toc: true
 number-sections: true
@@
 # Load data
-inst_data <- read.csv(here::here("outputs/data/inst_data_cleaned.csv"))
-
+inst_data <- read.csv(here::here("inputs/data/inst_data_cleaned.csv"))
 std_data <- read_csv(here::here("inputs/data/stdsurvey.csv"))
 
-# exp_data <- read.csv(here::here("inputs/data/experiment.csv"))
 ```
 
-# FIGURE 3
+# Introduction
 
-Our data (@tbl-figure3).
+It’s a heteronormative norm that we consider men to be assertive and leaderly, while women are nurturing and supportive.
+Often, women who choose to break out of these stereotypes and speak out against misogyny are labelled ‘emotional’ or ‘aggressive’, hindering their professional mobility [@AACSB].
+Even in academic settings, women tend to be penalized when achieving better grades.
+A study conducted by Natasha Quadlin, suggests that due to traditional, gendered stereotypes, women’s academic achievements are often disregarded compared to their male counterparts when both enter the labour market.
+Men of ‘high-achieving’ academic backgrounds tend to get favourable callbacks for interviews compared to their female counterparts within the same field [@SageJournals].
+
+This begs the question of whether these unequal tendencies exist in higher education for women, attempting to have their academic achievements recognized and improved by regrade requests.
+Many reasons can account for this gendered inequality.
+First, being subjected to societal norms, women tend to be more non-confrontational, resulting in them accepting their academic results as they are [@AACSB].
+Second, with differing confidence levels and personalities, women tend to second-guess their abilities, hence preventing them from requesting aid from their institutions as they see the entire process as ‘tedious’.
+Lastly, fear of rejection, women tend to harbour higher levels of stress and embarrassment when considering regrade requests as they assume that the result will often be a rejection [@SageJournals].
+A paper published by the American Journal of Political Science by Li and Zahar delves into the differences that arise between genders when requesting grade changes among college students from Colorado State University from 2010 to 2018.
+According to their findings, male students are more likely to request grade changes than their female counterparts, accounting for a whopping 18.6% higher of receiving a favourable grade change.
+Regardless of the class number, males are more likely to ask for grade changes throughout the semester [@InsideHigherEd].
+Overall there is a gender disparity among college students regarding regrade requests.
+Hence, by examining biases inherent within higher education, the paper contributes to understanding the power dynamics between two gender demographics.
+
+Our paper will reproduce, ‘Ask and You Shall Receive?
+Gender differences in Regrades in College’ by Li and Zafar.
+Accordingly, we ascertain that upon a regrade request, males are more likely to receive a favourable grade change.
+Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings?
+Are there fluctuations in regrade request patterns among male and female students regarding their class number?’ Structurally, our paper starts with a brief dissection of the original paper’s findings and our own interpretation of the data.
+Subsequently, we analyze the results garnered from the data with suitable tables, and double stacked bar charts.
+Finally, to conclude, we will discuss our findings, entailed by an analysis of the data’s loopholes, ethical biases and future research implications.
+
+Our replication package was sourced from the openICPSR Portal under the library `readstata13` package [@readStata13].
+We retrieved two datasets–‘instsurvey.dta’ and ‘stdsurvey.dta’– and one code file–‘1_FiguresTables.do’–from the data package ‘DataCode’ to examine gender identities of undergraduate students from Colorado State University from 2010 to 2018 and their correlation to regrade requests [@].
+Data was generated, extracted and cleaned using the open-source statistical programming language R [@r], leveraging functions from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], `janitor` [@rJanitor], `kableExtra` [@rKableExtra], and `knitr` [@rKnitr].
+
+# Data {#sec-data}
+
+Published by the ‘American Economic Journal: Economic Policy’, this paper reproduced the paper ‘Ask and You Shall Receive?
+Gender Differences in Regrades in College’ and its replication package published on `openICPSR` [cite].
+This data package conveys information related to survey data from instructors and students on the pervasiveness of regrade requests based on gender identities from 2010 to 2018.
+Particularly, ‘instsurvey.dta’ contains all 190 observations of actual regrade requests in 2018, along with 61 variables concerning the nature of each regrade request and whether or not each instance initiated grade changes.
+On the other hand, ‘stdsurvey.dta’ conveys all 3885 observations of student surveyees who have contemplated requesting regrades, with 52 variables detailing instances where they didn’t initiate such requests.
+With these two datasets representing two perspectives on regrade requests, there is much power dynamic to unpack, helping this paper assess the gendered nature of regrade requests in the undergraduate setting.
+
+## Instructor Survey Data
+
+Most prominent to our reproduction lies in the tactile grade changes of regrade requests based on each student’s gender identity.
+As such, we first simplified ‘instsurvey.dta’, which featured 190 observations.
+We cleaned the data by selecting relevant variables such as “maleup_fn”, “malesame_fn”, “maledown_fn”, “femaleup_fn”, “femalesame_fn”, “femaledown_fn”, “maleup_mt”, “malesame_mt”, “maledown_mt”, “femaleup_mt”, “femalesame_mt”, and “femaledown_mt”.
+The respective variables provide data on the number of male and female students whose grades increased, stayed the same or decreased both during and at the end of the semester.
+We further modified the data by calculating the mean of each variable using the mean() function.
+The mean is needed to determine the percentage of male or female students who received a grade increase, decrease, or no change.
+A new data frame is then created per focus area.
+In total four graphs were created to show the percentage of male and female students who received a grade increase, decrease, or no change after requesting for a regrade both during and at the end of the semester.
+
+## Student Survey Data
 
 ```{r}
-#| label: tbl-figure3
-#| tbl-cap: "Instructor Survey: Regrade Results by Timing and Students’ Gender"
+#| echo: false
+#| message: false
+#| label: tbl-genderclass
+#| tbl-cap: Cleaned Table of Number of Classes Students Considered for Regrade Requests by Students’ Gender
+
+classes_dta <- std_data |>
+              select(std_male, num_class, consider_regrade)|>
+              rename(Gender = std_male) |>
+              filter(is.na(consider_regrade) | consider_regrade != "No")
+
+classes_dta$consider_regrade[classes_dta$consider_regrade == "Yes"] <- "No"
+classes_dta$consider_regrade[is.na(classes_dta$consider_regrade)] <- "Yes"
+classes_dta$Gender[classes_dta$Gender == "1"] <- "Male"
+classes_dta$Gender[classes_dta$Gender == "0"] <- "Female"
+
+classes_dta <- classes_dta |>
+  group_by(num_class, Gender, consider_regrade) |>
+  count() |>
+  group_by(Gender, consider_regrade) |>
+  mutate(Percentage = round(n/sum(n)*100, 1))|>
+  mutate(num_class = case_match(num_class, 
+                             0 ~ "0 class",
+                             1 ~ "1 class",
+                             2 ~ "2 classes",
+                             3 ~ "3 classes",
+                             4 ~ "4 classes",
+                             5 ~ "5 classes"))
+
+classes_dta |>
+  filter(consider_regrade != "No") |>
+  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)
+head(classes_dta, 10) |>
+  kable(
+    col.names = c("Number of Classes", "Gender", "Consider Regrade", "Count", "Percentage"),
+    booktabs = TRUE,
+    align = c("c", "c", "c", "c", "c")
+  )
+
+```
+
+Conversely, the ‘stdsurvey.dta’ dataset featured 3885 observations of all potential regrade requests, which provided us with insights into gender identity and student psychology when approaching regrades.
+To simplify the data, we first clean its names and select relevant variables, including ‘std_male’, ‘consider_regrade’, ‘num_class’ and ‘participantcode’ which respectively convey data on students’ gender, whether or not they have considered regrading, the number of classes they have considered regrades and identification.
+For ‘std_male’, a ‘1’ signifies a male student while a ‘0’ signifies a female student; in which, to clean the dataset, we’ve renamed the column to ‘gender’ and modified ‘1’ to be ‘Male’ while ‘0’ to be ‘Female’.
+To garner data on students who considered regrading, we used `filter` to get rid of observations with ‘No’ for their ‘consider_regrade’ column.
+`mutate` was also leveraged to generate a column on ‘percentage’ of students who considered regrading ([@tbl-genderclass]).
+Proceedingly, we used the cleaned data to generate a double-stacked bar chart of the percentage of female and male students who considered regrading for each of the categories of the number of classes.
+
+# Results
+
+@fig-RegreadeResultsByTime explores the percentage of both male and female students who have had their grades unchanged, increased or decreased after requesting a regrade during and at the end of the semester.
+@fig-RegreadeResultsByTime-1 shows that 80% of male students have received no change in their grades at the end of the semester.
+Only 18% received a grade increase while 1% of male students received a grade decrease.
+
+@fig-RegreadeResultsByTime-2 shows that 79% of female students received no change in their grades at the end of the semester.
+However, 20% did receive a grade increase, which is a slight increase compared to male students.
+1% of female students received a grade decrease.
+
+Both @fig-RegreadeResultsByTime-1 and @fig-RegreadeResultsByTime-2 show that most students (male and female) received no change after requesting a regrade at the end of the semester.
+However, the data shows that female students had a higher percentage by 2% in receiving a grade increase compared to male students.
+Both male and female students had approximately 1% of regrade requests, resulting in a grade decrease.
+
+@fig-RegreadeResultsByTime-3 and @fig-RegreadeResultsByTime-4 show the change in grades of male and female students who ask for regrades during the semester.
+In @fig-RegreadeResultsByTime-3 the graph shows that 62% of male students received no change in their grade while 37% received a grade increase and approximately 1% received a grade decrease.
+@fig-RegreadeResultsByTime-4 shows that 59% of female students received no change in their grade while 40% had a grade increase and approximately 1% had a grade decrease when asking for a regrade during the semester.
+When comparing the results, 62% of male students received no change after requesting a regrade during the semester – 3% higher than female students.
+In addition, 40% of female students received an increase in their grade after requesting a regrade – 3% higher than male students.
+Both male and female students had approximately 1% of regrade requests, resulting in a grade decrease.
+
+```{r}
+#| label: fig-RegreadeResultsByTime
+#| fig-cap: Instructor Survey Regrade Results by Timing and Students’ Gender
+#| fig-subcap: [Panel A. End of semester male students, Panel B. End of semester female students, Panel C. During semester male students, Panel D. During semester female students]
+#| layout-ncol: 2
 #| warning: false
@@
   geom_text(aes(label = round(value)), vjust = -0.5, size = 3) +  # Add labels on top of bars
-  labs(title = "Panel A. End of semester, male students",
-       x = "Category",
+  labs(x = "Category",
        y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
@@
   geom_text(aes(label = round(value)), vjust = -0.5, size = 3) +  # Add labels on top of bars
-  labs(title = "Panel A. End of semester, female students",
-       x = "Category",
+  labs(x = "Category",
+       y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
+  scale_y_continuous(breaks = custom_breaks) +  # Set custom breaks for y-axis
+  theme_minimal()
+
+# During Semester Results MALE
+
+male_mt_dta <- inst_data |>
+              select(maleup_mt, malesame_mt, maledown_mt)
+
+maleup_mt_avg <- mean(male_mt_dta$maleup_mt, na.rm = TRUE)
+malesame_mt_avg <- mean(male_mt_dta$malesame_mt, na.rm = TRUE)
+maledown_mt_avg <- mean(male_mt_dta$maledown_mt, na.rm = TRUE)
+
+males_mt <- data.frame(
+  value = c(maleup_mt_avg, malesame_mt_avg, maledown_mt_avg),
+  category = c("Grade Increase", "No Change", "Grade Decrease")
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'category' variable to a factor with the specified order
+males_mt$category <- factor(males_mt$category, levels = category_order)
+
+# Set custom breaks for the y-axis
+custom_breaks <- seq(0, 90, by = 30)
+
+# Create a bar graph using ggplot
+ggplot(males_mt, aes(x = category, y = value, fill = category)) + ylim(0, 90) +
+  geom_bar(stat = "identity") +
+  geom_text(aes(label = round(value)), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(x = "Category",
+       y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
+  scale_y_continuous(breaks = custom_breaks) +  # Set custom breaks for y-axis
+  theme_minimal()
+
+# During Semester Results FEMALE
+
+female_mt_dta <- inst_data |>
+              select(femaleup_mt, femalesame_mt, femaledown_mt)
+
+femaleup_mt_avg <- mean(female_mt_dta$femaleup_mt, na.rm = TRUE)
+femalesame_mt_avg <- mean(female_mt_dta$femalesame_mt, na.rm = TRUE)
+femaledown_mt_avg <- mean(female_mt_dta$femaledown_mt, na.rm = TRUE)
+
+females_mt <- data.frame(
+  value = c(femaleup_mt_avg, femalesame_mt_avg, femaledown_mt_avg),
+  category = c("Grade Increase", "No Change", "Grade Decrease")
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'category' variable to a factor with the specified order
+females_mt$category <- factor(females_mt$category, levels = category_order)
+
+# Set custom breaks for the y-axis
+custom_breaks <- seq(0, 90, by = 30)
+
+# Create a bar graph using ggplot
+ggplot(females_mt, aes(x = category, y = value, fill = category)) + ylim(0, 90) +
+  geom_bar(stat = "identity") +
+  geom_text(aes(label = round(value)), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(x = "Category",
        y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
@@
 
-# FIGURE 2
-
-Figure 2. Student Survey: Number of Classes Students Considered for Regrade Requests by Students’ Gender
+Suceedingly, @fig-RegradeByClass shows the averaged distribution of the number of classes in which students are considered for regrades by gender.
+Observable in the graph, there is only data available on students who considered regrades in ‘0 class’ to ‘5 classes or more’ (CITE).
+Therefore, with the number of classes limited to 5, it’s more than likely that surveys understate the regraded data (CITE).
+Observably, with no or 0 classes, the majority of students didn’t consider regrade requests, with females upholding 41.2 % while males upholding 39.3%, making it a 1.9% difference.
+This trend of females considering for regrades is higher than males when the class number is lower, where at 1 class, a whopping 30.4% of females are considered for regrades in contrast to a meagre 22.7% of males.
+This translates to a huge margin of 7.7% between the two genders.
+However, as the number of classes extended above 1, or from 2 to 5 or more classes, more males considered asking for a regrade.
+For instance, at 3 classes, 8.9% of males considered for regrades as opposed to 7.1% of females; at 4 classes, 3.3% of males considered for regrades compared to 2% of females and finally, at 5 classes or more, a great 5.2% of males considered for regrades compared to a small 2.1% females.
+Statistically then, while the difference is negligible in some categories of class number, males are more likely to consider and ask for regrades compared to females (except for those with 1 class).
 
 ```{r}
-classes_dta <- std_data |>
-              select(std_male, num_class, consider_regrade)|>
-              rename(Gender = std_male) |>
-              filter(is.na(consider_regrade) | consider_regrade != "No")
-
-classes_dta <- classes_dta |>
-  group_by(num_class, Gender, consider_regrade) |>
-  count() |>
-  group_by(Gender, consider_regrade) |>
-  mutate(Percentage = round(n/sum(n)*100, 1))|>
-  mutate(num_class = case_match(num_class, 
-                             0 ~ "0 class",
-                             1 ~ "1 class",
-                             2 ~ "2 classes",
-                             3 ~ "3 classes",
-                             4 ~ "4 classes",
-                             5 ~ "5 classes"))
-
-classes_dta$consider_regrade[classes_dta$consider_regrade == "Yes"] <- "No"
-classes_dta$consider_regrade[is.na(classes_dta$consider_regrade)] <- "Yes"
-classes_dta$Gender[classes_dta$Gender == "1"] <- "Male"
-classes_dta$Gender[classes_dta$Gender == "0"] <- "Female"
-
-classes_dta |>
-  filter(consider_regrade != "No") |>
-  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)
-head(classes_dta, 10) |>
-  kable(
-    col.names = c("Number of Classes", "Gender", "Consider Regrade", "Count", "Percentage"),
-    booktabs = TRUE,
-    align = c("c", "c", "c", "c", "c")
-  )
+#| label: fig-RegradeByClass
+#| fig-cap: Student Survey Number of Classes Students Considered for Regrade Requests by Students’ Gender
+#| warning: false
+#| message: false
+#| echo: false
 
@@
 
-# Introduction
-
-<intro>
-
-# Data {#sec-data}
-
-<data>
-
-# Model
-<model>
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
 # Discussion
 
-## First discussion point {#sec-first-point}
+The original paper looked to analyze the gender difference in a college setting upon regrade requests.
+The main questions Li and Zahar analyzed were whether male students are more frequent in their regrade requests compared to their female counterparts.
+The authors also look to analyze whether these requests result in favorable outcomes for either gender.
+By replicating this paper we look to understand the gender differences in favourable regrade requests with factors of course load and request frequencies throughout the semester.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Male and Female Regrade Outcomes
 
-## Second discussion point
+One key point to consider is the disparity in outcomes between male and female students when requesting a regrade.
+The data shows that a higher percentage of male students (62%) received no change in their grade after requesting a regrade during the semester compared to female students (59%).
+This explains the notion that males typically send out higher requests of regrades compared to their female counterparts.
+This could be attributed to the social implications placed on each gender, confirming the concept that men are more assertive hence their inclination to ask for regrades.
+Women are more accepting hence they refrain from attempting to submit a request.
+When looking at the percentage of students who did receive an increase in their grade after requesting a regrade, it turns out that a higher proportion of female students (40%) experienced this outcome compared to male students (37%).
+This suggests that, although male students were less successful overall in achieving grade changes when changes did occur, they were slightly more likely to increase for female students.
+Statistically, this 3% difference in outcomes, does not explain a great deal regarding the skewed gender implications but further research is required to understand the broader implications.
 
-## Third discussion point
+## Trends Among Female Students and Course Load
 
-## Weaknesses and next steps
+Another trend suggests that regrade consideration between male and female students is attributed to the number of courses they are taking.
+Female students are more inclined to submit regrade requests when taking fewer courses as 30.4% consider a regrade request when taking one course, while male students consideration is around 22.7%.
+However, when the course load is higher the trend is reversed.
+More male students submit or consider regrade requests compared to their female counterparts.
+At three classes, 8.9% of males consider regrades compared to 7.1% of females, and at five classes or more, 5.2% of males consider regrades compared to only 2.1% of females.
 
-Weaknesses and next steps should also be included.
+This trend suggests that males are more likely to consider and ask for regrades compared to females in all categories of classes, except for those with 1 class.
+This translates to the fact that, speculatively, males are more likely to consider for regrades regardless of and in more circumstances than females.
+This is a factor for consideration, especially taking into account gender expectations regarding assertiveness and social boundaries when it comes to asking for more, and in this context, asking for more grades.
+Vice versa, females on average are only likely to ask for regrade in one class even if they have more than one class that necessitates regrade consideration.
+This trend could be attributed to the notion that with 1 course, more investment is required hence the motivation to work harder.
+Compared to a higher course load which requires time management and balance.
 
-\newpage
+Further analysis could explore potential reasons behind these disparities, such as differences in the types of courses taken by male and female students, variations in grading criteria, or individual attitudes toward requesting grade changes.
 
-\appendix
+## Ethics and Biases
 
-# Appendix {-}
+To note, there are further pain points regarding the gendered nature of the dataset, making the analysis reductive.
+Previous research has remarked on the discrimination against people of sexual minority background in educational settings (LGBTQI+), which poses considerable alarm on how they would be unfavourable when it comes to regrade requests in a college setting as well [@WilliamsInstitute].
+However, the study only assesses regrade requests from a binary, gendered perspective since the participants identified as either males or females.
+This thus limits the study’s assessment of those who identify as non-binary, two-spirited or gender-fluid.
+Accordingly, we recognize that simplifying the gender spectrum to a mere binary of males and females can disregard the struggles non-binary people have against college discrimination (or re-grading in this paper’s context).
+Contextually, the original study simulates a classroom setting within a closed laboratory to survey the implications of regrade requests.
+The study thus requires participants to perform their student identity and imitate their regrade request scenarios, which could have posited the students to have a ‘formal”, heteronormative identity to fit in with the study’s nature.
+This method thus could have influenced student behaviours.
+It drives students away from a typical scenario of regrade requests, where there is a big power difference between a student and an actual professor.
+This, in many ways, denaturalized the nature of regrade requests and affected the study’s results.
 
-# Additional data details
+## Limitations
 
-# Model details {#sec-model-details}
+Since this paper was a replication, our analysis was limited to results and interpretations made by Li and Zahar from the original paper.
+We decided to focus on one aspect of the paper rather than having the time to explore the other possible relationships with the data.
+If we had additional time and resources we would have liked to see the other findings within Li and Zahar’s paper regarding payments and regarding requests in the lab and how those data sets relate to ours.
+If we had additional time and resources, we would have expanded our investigation to include other findings from Li and Zahar's paper, particularly those related to the positive social costs of regrade requests and lab requirements.
+These additional insights could provide a more comprehensive understanding of the dynamics surrounding grade regrade requests among college students.
+By incorporating these findings, we could further elucidate the factors influencing students' behaviours and outcomes in academic settings, contributing to a richer and more nuanced analysis of gender disparities within academia.
 
-## Posterior predictive check
+As mentioned previously, the exclusion of non-binary people could have affected the data collected and impacted the validity.
+Given their status as an underrepresented group, their perspectives are overlooked, leading to a potential bias in the results.
+This oversight not only limits the results but the generalization towards a population is skewed.
+Another limitation was during the replication process the replicated graphs did not produce the identical results as the graphs from the original paper.
+Instead, the results in the replicated graphs are different from 1-2%.
+We are not sure why the results are different as the same dataset from the original graph was used to replicate.
+We assume the cause for this distortion can be attributed to the different logic used in R rather than Stata.
+
+# Future
+
+Future studies should aim to investigate the broader implications of gender inequalities in academic settings and how those trends translate into the labour market.
+Particularly looking at the females and their ability to secure jobs in the same field as their male counterparts.
+Understanding these gender biases in the labour force and academics provides valuable insight into how these gender disparities continue to persist.
+Moreover, studies regarding the long-term consequences of these trends should be conducted to understand the psychological implications.
+Observing how gender biases affect students’ confidence, motivation and overall well-being can help contribute to the understanding of the challenges faced by marginalized groups.
+Additionally, exploring the intersectionality between factors such as race, ethnicity, socioeconomic status and sexual orientation can provide a holistic understanding of systemic biases and inequity in academia.
 

### 2024-02-14 scripts/00-simulate_data.R

@@ -1,19 +1,213 @@
 #### Preamble ####
-# Purpose: Simulates 
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates dataset of correlation between gender identities and regrades among undergraduate students, 2010-2016 
+# Author: Quang Mai, Catherine Punnoose and Faiza Imam
+# Date: 12 February 2024 
+# Contact:
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
+
+#### Data Expectations ####
+# Number of classes that students  events divided by gender and race
+# Expect different types of clinics, like city-run, hospital, pharmacy, pop-ups
+# Opening date should be a valid date before today
+# columns: clinic_id, district, type, opening_date
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Simulate data ####
-# [...ADD CODE HERE...]
+library(janitor)
 
 
+#### Simulate the number of classes students considered for regrade requests by students' gender 
+# Code referenced from from: https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html#simulate
 
+set.seed(97) #ensure simulated data's reproducibility
+
+simulated_data <-
+  tibble(
+    #use 1 through 65276 to represent each arrest event
+    "id" = 1:3885,
+    #randomly pick a the number of classes identified from the dataset, with replacement, 65276 times
+    "num_class" = sample(
+      x = c("0 class", "1 class", "2 classes", "3 classes", "4 classes", "5 classes"),
+      size = 3885,
+      replace = TRUE
+    ),
+    #randomly pick one gender identity identified from the dataset, with replacement, 65276 times
+    "gender" = sample(
+      x = c("Male", "Female"),
+      size = 3885,
+      replace = TRUE
+    ),
+    #randomly pick whether the student considers regrade, with replacement, 65276 times
+    "consider_regrade" = sample(
+      x = c("Yes", "No"),
+      size = 3885,
+      replace = TRUE
+    )
+  )
+
+
[…]

### 2024-02-14 scripts/02-data_cleaning.R

@@ -16,16 +16,15 @@ library(tidyverse)
 ### CLEANING DATA ###
 ### Cleaning Instructor	Survey	Data (instsurvey) ###
 # Read data
-#inst_data <- read.csv(here::here("inputs/data/instsurvey.csv"))
-
 inst_data <- read.csv("inputs/data/instsurvey.csv")
 
 inst_data_cleaned <- 
   inst_data |>
   janitor::clean_names() |>
-  select(id, maleup_fn, femaleup_fn, malesame_fn, femalesame_fn, maledown_fn, femaledown_fn) |>
+  select(id, maleup_fn, femaleup_fn, malesame_fn, femalesame_fn, maledown_fn, femaledown_fn, maleup_mt, femaleup_mt, malesame_mt, femalesame_mt, maledown_mt, femaledown_mt) |>
   tidyr::drop_na()
 
+#### Save Clean Instsurvey data ####
 write_csv(inst_data_cleaned, "inputs/data/inst_data_cleaned.csv")
 
 ### Cleaning Stdsurvey ###
@@ -36,13 +35,7 @@ std_data_cleaned <-
   janitor::clean_names() |>
   select(participantcode, std_female, std_standing, std_male, consider_regrade, everasked, num_class, num_asked)
 
-
-
 #### Save Clean Stdsurvey data ####
 write_csv(std_data_cleaned, "inputs/data/std_data_cleaned.csv")
-
-### Cleaning Experiment ###
-#exp_data <- read.csv(here::here("inputs/data/experiment.csv"))
-
 
 

### 2024-02-14 scripts/03-test_data.R

@@ -37,7 +37,6 @@ inst_data_cleaned$maledown_fn |> min() == 0
 inst_data_cleaned$femaledown_fn |> min() == 0
 
 
-
 # Test 2: check that the std dataset's num_class variable and see if it has minium 0 class and maximum 5 classes
 std_data_cleaned$num_class |> min() == 0
 std_data_cleaned$num_class |> max() == 5

### 2024-02-14 outputs/paper/paper.qmd
finalize paper

@@
 author: Faiza Imam, Quang Mai & Catherine Punnoose 
-thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git"
+thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: 10.1257/pol.20210053"
 date: today
@@
 #| include: false
+#| echo: false
 #| warning: false
@@
 std_data <- read_csv(here::here("inputs/data/stdsurvey.csv"))
-
 ```
@@
 Our replication package was sourced from the openICPSR Portal under the library `readstata13` package [@readStata13].
-We retrieved two datasets–‘instsurvey.dta’ and ‘stdsurvey.dta’– and one code file–‘1_FiguresTables.do’–from the data package ‘DataCode’ to examine gender identities of undergraduate students from Colorado State University from 2010 to 2018 and their correlation to regrade requests [@].
+We retrieved two datasets–‘instsurvey.dta’ and ‘stdsurvey.dta’– and one code file–‘1_FiguresTables.do’–from the data package ‘DataCode’ to examine gender identities of undergraduate students from Colorado State University from 2010 to 2018 and their correlation to regrade requests [@GenderDiff].
 Data was generated, extracted and cleaned using the open-source statistical programming language R [@r], leveraging functions from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], `janitor` [@rJanitor], `kableExtra` [@rKableExtra], and `knitr` [@rKnitr].
@@
 
+```{R}
+#| echo: false
+#| message: false
+#| label: tbl-genderTime
+#| tbl-cap: Table of Instructor Survey Regrade Results by Timing and Students’ Gender
+
+# Male Final Grade Data
+cleanInstData <- data.frame(
+  maleup_avg =  mean(inst_data$maleup_fn, na.rm = TRUE), 
+  malesame_avg = mean(inst_data$malesame_fn, na.rm = TRUE), 
+  maledown_avg = mean(inst_data$maledown_fn, na.rm = TRUE)
+)
+
+cleanInstData |>
+  kable(
+    col.names = c("Male: Final Grade Increase ", "Male: Final Grade Same ", "Male: Final Grade Decrease ") , 
+    align = c("c", "c", "c")
+  )
+
+# Female Final Grade Data
+cleanInstData <- data.frame(
+  femaleup_avg =  mean(inst_data$femaleup_fn, na.rm = TRUE), 
+  femalesame_avg = mean(inst_data$femalesame_fn, na.rm = TRUE), 
+  femaledown_avg = mean(inst_data$femaledown_fn, na.rm = TRUE)
+)
+
+cleanInstData |>
+  kable(
+    col.names = c("Female: Final Grade Increase ", "Female: Final Grade Same ", "Female: Final Grade Decrease "),
+    align = c("c", "c", "c")
+  )
+
+# Male During Semester Grade Data
+cleanInstData <- data.frame(
+  maleup_mt_avg  =  mean(inst_data$maleup_mt, na.rm = TRUE), 
+  malesame_mt_avg = mean(inst_data$malesame_mt, na.rm = TRUE), 
+  maledown_mt_avg = mean(inst_data$maledown_mt, na.rm = TRUE)
+)
+
+cleanInstData |>
+  kable(
+    col.names = c("Male: During Semester Grade Increase ", "Male: During Semester Grade Same ", "Male: During Semester Grade Decrease ") , 
+    align = c("c", "c", "c")
+  )
+
+# Female During Semester Grade Data
+cleanInstData <- data.frame(
+  femaleup_mt_avg  =  mean(inst_data$femaleup_mt, na.rm = TRUE), 
+  femalesame_mt_avg = mean(inst_data$femalesame_mt, na.rm = TRUE), 
+  femaledown_mt_avg = mean(inst_data$femaledown_mt, na.rm = TRUE)
+)
+
+cleanInstData |>
+  kable(
+    col.names = c("Female: During Semester Grade Increase ", "Female: During Semester Grade Same ", "Female: During Semester Grade Decrease ") , 
+    align = c("c", "c", "c")
+  )
+
+```
+
 ## Student Survey Data
@@
 #| label: tbl-genderclass
-#| tbl-cap: Cleaned Table of Number of Classes Students Considered for Regrade Requests by Students’ Gender
+#| tbl-cap: Table of Number of Classes Students Considered for Regrade Requests by Students’ Gender
 
@@
   filter(is.na(consider_regrade) | consider_regrade != "No")
-
-classes_dta$consider_regrade[classes_dta$consider_regrade == "Yes"] <- "No"
-classes_dta$consider_regrade[is.na(classes_dta$consider_regrade)] <- "Yes"
-classes_dta$Gender[classes_dta$Gender == "1"] <- "Male"
-classes_dta$Gender[classes_dta$Gender == "0"] <- "Female"
 
@@
 
+classes_dta$consider_regrade[classes_dta$consider_regrade == "Yes"] <- "No"
+classes_dta$consider_regrade[is.na(classes_dta$consider_regrade)] <- "Yes"
+classes_dta$Gender[classes_dta$Gender == "1"] <- "Male"
+classes_dta$Gender[classes_dta$Gender == "0"] <- "Female"
+
 classes_dta |>
   filter(consider_regrade != "No") |>
-  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)
-head(classes_dta, 10) |>
+  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade) |>
+  head(12) |>
   kable(
@@
   scale_y_continuous(breaks = custom_breaks) +  # Set custom breaks for y-axis
-  theme_minimal()
+  theme_minimal() + theme(legend.position = "bottom")
 

### 2024-02-14 outputs/paper/paper.qmd
clarify estimand

@@
 Gender differences in Regrades in College’ by Li and Zafar.
-Accordingly, we ascertain that upon a regrade request, males are more likely to receive a favourable grade change.
+Accordingly, our estimand asserts that upon a regrade request, males are more likely to receive a favourable grade change regardless of the time during the semester, and regardless of the number of classes that they have.
 Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings?

### 2024-02-14 outputs/paper/paper.qmd
finalize formatting

@@
 ---
-title: "The Relationship Between Gender Identities and Regrades among Undergraduate Students, 2010-2016"
+title: "Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016"
 subtitle: "A replication of Li and Zahar;"
@@
 Suceedingly, @fig-RegradeByClass shows the averaged distribution of the number of classes in which students are considered for regrades by gender.
-Observable in the graph, there is only data available on students who considered regrades in ‘0 class’ to ‘5 classes or more’ (CITE).
-Therefore, with the number of classes limited to 5, it’s more than likely that surveys understate the regraded data (CITE).
+Observable in the graph, there is only data available on students who considered regrades in ‘0 class’ to ‘5 classes or more’ ([@fig-RegradeByClass]).
+Therefore, with the number of classes limited to 5, it’s more than likely that surveys understate the regraded data [@GenderDiff].
 Observably, with no or 0 classes, the majority of students didn’t consider regrade requests, with females upholding 41.2 % while males upholding 39.3%, making it a 1.9% difference.

### 2024-02-14 outputs/paper/paper.qmd
finalize paper

@@
 date-format: long
-abstract: "Academia is a complex ecosystem that feeds off a network of social, cultural and innovative influences which often, stem beyond societal norms.
-This paper replicates the gender implications regarding results in college students and explores potential fluctuations in request patterns over a semester by specifically analyzing the number of classes taken by students and their willingness to submit a grade request throughout the semester.
-Our results show that there is a trend for female students to submit regrade requests while taking fewer courses compared to a higher course load.
-Female students experienced grade increases (3%) compared to their male counterparts.
-We call for further investigation around this topic to understand gender disparities within the world of academia.
+abstract: "Institutionalized and traditional, academia often exacerbates gender differences.
+This paper then replicates the gender implications behind regrade requests of undergraduate students in Colorado State University from 2010-2016.
+By analyzing the number of classes taken by students, their willingness to request regrade and actual grade changes, this paper explores fluctuations in regrade request patterns throughout the semester.
+Our results show that on average males students are more likely to submit regrade requests, and-even when they request regrade for more courses-still have better grade changes compared to female students.
+We thus call for further investigation around this topic to understand gender disparities within the world of academia.
 "

### 2024-02-14 outputs/paper/paper.qmd
finalize paper

@@
 Our results show that on average males students are more likely to submit regrade requests, and-even when they request regrade for more courses-still have better grade changes compared to female students.
-We thus call for further investigation around this topic to understand gender disparities within the world of academia.
-"
+We thus call for further investigation around this topic to understand gender disparities within the world of academia."
 format: pdf

### 2024-02-19 scripts/02-data_cleaning.R
Updated 02-data_cleaning.R preamble

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
+# Purpose: Clean up the survey.dta from https://doi.org/10.7910/DVN/QXJDJ5. Specifically selecting columns participantcode, std_female, std_standing, std_male, consider_regrade, everasked, num_class, num_asked).
 # Author: Catherine Punnoose, Quang Mai, Faiza Imam 
 # Date: 13 Feb 2024 
 # Contact: catherine.punnoose@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 01-download_data.R
 
 #### Workspace setup ####
 library(dplyr)

### 2024-02-20 outputs/paper/paper.qmd
Updates

@@
 title: "Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016"
-subtitle: "A replication of Li and Zahar;"
 author: Faiza Imam, Quang Mai & Catherine Punnoose 
-thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: 10.1257/pol.20210053"
+thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: https://doi.org/10.48152/ssrp-bjze-cn68"
 date: today
 date-format: long
-abstract: "Institutionalized and traditional, academia often exacerbates gender differences.
-This paper then replicates the gender implications behind regrade requests of undergraduate students in Colorado State University from 2010-2016.
-By analyzing the number of classes taken by students, their willingness to request regrade and actual grade changes, this paper explores fluctuations in regrade request patterns throughout the semester.
-Our results show that on average males students are more likely to submit regrade requests, and-even when they request regrade for more courses-still have better grade changes compared to female students.
-We thus call for further investigation around this topic to understand gender disparities within the world of academia."
+abstract: "Academia often exacerbates gender differences.
+This paper further explores the gender implications behind regrade requests of undergraduate students at Colorado State University from 2010-2016.
+By analyzing changes in regrade request patterns throughout the semester, actual grade changes, and instructor’s gender identity, our results show that on average male students are more likely to submit regrade requests, and are more likely–even when they request regrade for more courses–to have better grade changes compared to female students.
+In addition, extrapolation on the original study seems to suggest that both female and male instructors are more likely to give out favourable regrades for female students, which raises interesting questions on gender dynamics and regrading in the college setting."
 format: pdf
+fig-pos: 'H'
 toc: true
@@
 std_data <- read_csv(here::here("inputs/data/stdsurvey.csv"))
+inst_data_cleaned <- read_csv(here::here("inputs/data/inst_data_cleaned.csv"))
 ```
 
-# Introduction
+# Introduction {#sec-intro}
 
-It’s a heteronormative norm that we consider men to be assertive and leaderly, while women are nurturing and supportive.
-Often, women who choose to break out of these stereotypes and speak out against misogyny are labelled ‘emotional’ or ‘aggressive’, hindering their professional mobility [@AACSB].
-Even in academic settings, women tend to be penalized when achieving better grades.
+It’s a societal norm that we consider men to be assertive and dominant in leadership roles while women are nurturing and supportive.
+Often, women who choose to break out of these stereotypes and speak out against misogyny and sexism are labelled ‘emotional’ or ‘aggressive’, hindering their professional mobility [@AACSB].
+Even in academic settings, women tend to be penalized when achieving better grades and opportunities.
 A study conducted by Natasha Quadlin, suggests that due to traditional, gendered stereotypes, women’s academic achievements are often disregarded compared to their male counterparts when both enter the labour market.
-Men of ‘high-achieving’ academic backgrounds tend to get favourable callbacks for interviews compared to their female counterparts within the same field [@SageJournals].
+Men of ‘high-achieving’ academic backgrounds tend to get favourable callbacks for interviews compared to their female counterparts with the same credentials [@SageJournals].
 
-This begs the question of whether these unequal tendencies exist in higher education for women, attempting to have their academic achievements recognized and improved by regrade requests.
-Many reasons can account for this gendered inequality.
-First, being subjected to societal norms, women tend to be more non-confrontational, resulting in them accepting their academic results as they are [@AACSB].
-Second, with differing confidence levels and personalities, women tend to second-guess their abilities, hence preventing them from requesting aid from their institutions as they see the entire process as ‘tedious’.
-Lastly, fear of rejection, women tend to harbour higher levels of stress and embarrassment when considering regrade requests as they assume that the result will often be a rejection [@SageJournals].
+This begs whether these unequal tendencies exist in higher education for women, as they attempt to have their academic achievements recognized by requesting regrades.
+There are many reasons to account for when analyzing gendered inequality.
+First, being subjected to societal norms, women tend to be more non-confrontational, resulting in them accepting their academic results as they are instead of fighting for them [@AACSB].
+Second, with differing confidence levels and personalities, women tend to second-guess their abilities, hence preventing them from requesting aid from their institutions as they see the entire process as ‘tedious’ and “unnecessary’ [@SageJournals].
+Lastly, fear of rejection, women tend to harbour higher levels of stress and embarrassment when considering regrade requests as they assume that the result will often be a rejection from their instructors [@SageJournals].
 A paper published by the American Journal of Political Science by Li and Zahar delves into the differences that arise between genders when requesting grade changes among college students from Colorado State University from 2010 to 2018.
-According to their findings, male students are more likely to request grade changes than their female counterparts, accounting for a whopping 18.6% higher of receiving a favourable grade change.
+According to their findings, male students are more likely to request grade changes than their female counterparts, accounting for 18.6% higher of receiving a favourable grade change.
 Regardless of the class number, males are more likely to ask for grade changes throughout the semester [@InsideHigherEd].
@@
 Hence, by examining biases inherent within higher education, the paper contributes to understanding the power dynamics between two gender demographics.
+In addition, to extrapolate from the original paper, our paper combines the student regrade data with instructors’ gender to see if there is gender dynamics between the two.
 
-Our paper will reproduce, ‘Ask and You Shall Receive?
-Gender differences in Regrades in College’ by Li and Zafar.
-Accordingly, our estimand asserts that upon a regrade request, males are more likely to receive a favourable grade change regardless of the time during the semester, and regardless of the number of classes that they have.
-Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings?
-Are there fluctuations in regrade request patterns among male and female students regarding their class number?’ Structurally, our paper starts with a brief dissection of the original paper’s findings and our own interpretation of the data.
-Subsequently, we analyze the results garnered from the data with suitable tables, and double stacked bar charts.
-Finally, to conclude, we will discuss our findings, entailed by an analysis of the data’s loopholes, ethical biases and future research implications.
+Thus, from the paper, ‘Ask and You Shall Receive?
+Gender differences in Regrades in College’ by Li and Zafar, we hope to look into the estimand that upon a regrade request, whether or not an instructor’s gender identity–when interacted with a student’s gender identity– affects the outcome of such a student’s re-grading.
+Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings?’, ‘Are there fluctuations in regrade request patterns among male and female students regarding their class number?’ and ‘Is there a correlation between instructor's gender and the regrading process?’
+
+Structurally, in @sec-intro, our paper starts with a brief dissection of the original paper’s findings and our interpretation of the data.
+Subsequently, in @sec-data and @sec-results, we analyze the results garnered from the data with suitable tables and double-stacked bar charts.
+Finally, to conclude, we will discuss our findings in @sec-discussion, which entailed an analysis of the data’s loopholes, ethical biases and future research implications.
 
@@
 Published by the ‘American Economic Journal: Economic Policy’, this paper reproduced the paper ‘Ask and You Shall Receive?
-Gender Differences in Regrades in College’ and its replication package published on `openICPSR` [cite].
+Gender Differences in Regrades in College’ and its replication package published on `openICPSR` [@openICPSR].
 This data package conveys information related to survey data from instructors and students on the pervasiveness of regrade requests based on gender identities from 2010 to 2018.
@@
 As such, we first simplified ‘instsurvey.dta’, which featured 190 observations.
-We cleaned the data by selecting relevant variables such as “maleup_fn”, “malesame_fn”, “maledown_fn”, “femaleup_fn”, “femalesame_fn”, “femaledown_fn”, “maleup_mt”, “malesame_mt”, “maledown_mt”, “femaleup_mt”, “femalesame_mt”, and “femaledown_mt”.
-The respective variables provide data on the number of male and female students whose grades increased, stayed the same or decreased both during and at the end of the semester.
+We cleaned the data by selecting relevant variables such as “maleup_fn”, “malesame_fn”, “maledown_fn”, “femaleup_fn”, “femalesame_fn”, “femaledown_fn”, “maleup_mt”, “malesame_mt”, “maledown_mt”, “femaleup_mt”, “femalesame_mt”, “femaledown_mt” and “inst_gender”.
+The respective variables provide data on the number of male and female students whose grades increased, stayed the same or decreased both during and at the end of the semester along with the instructor’s gender in each case.
 We further modified the data by calculating the mean of each variable using the mean() function.
@@
 In total four graphs were created to show the percentage of male and female students who received a grade increase, decrease, or no change after requesting for a regrade both during and at the end of the semester.
+
+Further, to analyze the differences in favourable regrades between male and female instructors, we renamed the original variable, “inst_female”  into “inst_gender”.
+We also changed “0” into “Male” and “1” into “Female to clarify the dataset.
+After that, we attempt to create four bar graphs to assess the correlation between instructors’ gender identity and favourable grade increases.
 
@@
 
+Conversely, the ‘stdsurvey.dta’ dataset featured 3885 observations of all potential regrade requests, which provided us with insights into gender identity and student psychology when approaching regrades.
+To simplify the data, we first clean its names and select relevant variables, including ‘std_male’, ‘consider_regrade’, ‘num_class’ and ‘participantcode’ which respectively convey data on students’ gender, whether or not they have considered regrading, the number of classes they have considered regrades and identification.
+For ‘std_male’, a ‘1’ signifies a male student while a ‘0’ signifies a female student; in which, to clean the dataset, we’ve renamed the column to ‘gender’ and modified ‘1’ to be ‘Male’ while ‘0’ to be ‘Female’.
+To garner data on students who considered regrading, we used `filter` to get rid of observations with ‘No’ for their ‘consider_regrade’ column.
+`mutate` was also leveraged to generate a column on ‘percentage’ of students who considered regrading ([@tbl-genderclass]).
+Proceedingly, we used the cleaned data to generate a double-stacked bar chart of the percentage of female and male students who considered regrading for each category of the number of classes.
+
 ```{r}
@@
 
+# Selecting required data 
 classes_dta <- std_data |>
@@
 
+# Cleaning classes_dta 
 classes_dta <- classes_dta |>
@@
   mutate(Percentage = round(n/sum(n)*100, 1))|>
-  mutate(num_class = case_match(num_class, 
+  mutate(num_class = case_match(num_class,     # mutating data so it is easier to understand 
                                 0 ~ "0 class",
@@
 
+# Creating a Table of classes_dta
 classes_dta |>
@@
 
-Conversely, the ‘stdsurvey.dta’ dataset featured 3885 observations of all potential regrade requests, which provided us with insights into gender identity and student psychology when approaching regrades.
-To simplify the data, we first clean its names and select relevant variables, including ‘std_male’, ‘consider_regrade’, ‘num_class’ and ‘participantcode’ which respectively convey data on students’ gender, whether or not they have considered regrading, the number of classes they have considered regrades and identification.
-For ‘std_male’, a ‘1’ signifies a male student while a ‘0’ signifies a female student; in which, to clean the dataset, we’ve renamed the column to ‘gender’ and modified ‘1’ to be ‘Male’ while ‘0’ to be ‘Female’.
-To garner data on students who considered regrading, we used `filter` to get rid of observations with ‘No’ for their ‘consider_regrade’ column.
-`mutate` was also leveraged to generate a column on ‘percentage’ of students who considered regrading ([@tbl-genderclass]).
-Proceedingly, we used the cleaned data to generate a double-stacked bar chart of the percentage of female and male students who considered regrading for each of the categories of the number of classes.
-
-# Results
+# Results {#sec-results}
 
@@
 #| echo: false
+#| fig-pos: "t"
 
 #Code Assisted from Chat GPT 3.5
-# End of Semester Results MALE
 
+# FIGURE 1A: End of Semester Results MALE Bar Graph
+
+# Selecting data on final grades for male students 
 male_dta <- inst_data |>
@@
 
+# Calculating average of grade increase, no change, and decrease for male students 
 maleup_avg <- mean(male_dta$maleup_fn, na.rm = TRUE)
@@
 
+# Creating new frame with selected data 
 males <- data.frame(
@@
   labs(x = "Category",
-       y = "Percent") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
+       y = "Percent", fill = "Category") + scale_fill_manual(values = c("Grade Increase" = "#4B659D", "No Change" = "#A83B48", "Grade Decrease" = "#B7BA9F")) +  # Adjust colors
   scale_y_continuous(breaks = custom_breaks) +  # Set custom breaks for y-axis
@@
 
-# End of Semester Results FEMALE
+# FIGURE 1B: End of Semester Results FEMALE Bar Graph
 
+# Selecting data on final grades for female students 
 female_dta <- inst_data |>
@@
 
+# Calculating average of grade increase, no change, and decrease for female students 
 femaleup_avg <- mean(female_dta$femaleup_fn, na.rm = TRUE)
@@
 
+# Creating new frame with selected data 
 females <- data.frame(
@@
 
-# During Semester Results MALE
+# FIGURE 1C: During Semester Results MALE Bar Graph
 
+# Selecting data of grades during the semester for male students 
 male_mt_dta <- inst_data |>
@@
 
+# Calculating average of grade increase, no change, and decrease for male students 
 maleup_mt_avg <- mean(male_mt_dta$maleup_mt, na.rm = TRUE)
@@
 
+# Creating new data frame with selected data
 males_mt <- data.frame(
@@
 
-# During Semester Results FEMALE
+# FIGURE 1D: During Semester Results FEMALE Bar Graph
 
+# Selecting data of grades during the semester for female students 
 female_mt_dta <- inst_data |>
@@
 
+# Calculating average of grade increase, no change, and decrease for female students 
 femaleup_mt_avg <- mean(female_mt_dta$femaleup_mt, na.rm = TRUE)
@@
 
+# Creating new data frame with selected data
 females_mt <- data.frame(
@@
 
-Suceedingly, @fig-RegradeByClass shows the averaged distribution of the number of classes in which students are considered for regrades by gender.
+@fig-RegradeByClass shows the averaged distribution of the number of classes in which students are considered for regrades by gender.
 Observable in the graph, there is only data available on students who considered regrades in ‘0 class’ to ‘5 classes or more’ ([@fig-RegradeByClass]).
@@
 Observably, with no or 0 classes, the majority of students didn’t consider regrade requests, with females upholding 41.2 % while males upholding 39.3%, making it a 1.9% difference.
-This trend of females considering for regrades is higher than males when the class number is lower, where at 1 class, a whopping 30.4% of females are considered for regrades in contrast to a meagre 22.7% of males.
+This trend of females considering for regrades is higher than males when the class number is lower, where at 1 class, 30.4% of females are considered for regrades in contrast to  22.7% of males.
 This translates to a huge margin of 7.7% between the two genders.
+
 However, as the number of classes extended above 1, or from 2 to 5 or more classes, more males considered asking for a regrade.
 For instance, at 3 classes, 8.9% of males considered for regrades as opposed to 7.1% of females; at 4 classes, 3.3% of males considered for regrades compared to 2% of females and finally, at 5 classes or more, a great 5.2% of males considered for regrades compared to a small 2.1% females.
-Statistically then, while the difference is negligible in some categories of class number, males are more likely to consider and ask for regrades compared to females (except for those with 1 class).
+Statistically then, while the difference is negligible in some categories of the class number, males are more likely to consider and ask for regrades compared to females (except for those with 1 class).
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-The original paper looked to analyze the gender difference in a college setting upon regrade requests.
-The main questions Li and Zahar analyzed were whether male students are more frequent in their regrade requests compared to their female counterparts.
-The authors also look to analyze whether these requests result in favorable outcomes for either gender.
-By replicating this paper we look to understand the gender differences in favourable regrade requests with factors of course load and request frequencies throughout the semester.
+The original paper looked to analyze the gender differences among undergraduate students upon regrade requests.
+The main question Li and Zahar analyzed was whether these requests result in favourable outcomes for either gender.
+To extrapolate on the original findings, we look to understand if the gender differences in regrade requests also correlate with the gender identity of the regrading instructors.
 
@@
 This could be attributed to the social implications placed on each gender, confirming the concept that men are more assertive hence their inclination to ask for regrades.
-Women are more accepting hence they refrain from attempting to submit a request.
-When looking at the percentage of students who did receive an increase in their grade after requesting a regrade, it turns out that a higher proportion of female students (40%) experienced this outcome compared to male students (37%).
+Women are more accepting hence they refrain from attempting to submit a request [@AACSB].
+When looking at the percentage of students who received an increase in their grade after requesting a regrade, it turns out that a higher proportion of female students (40%) experienced this outcome than male students (37%).
 This suggests that, although male students were less successful overall in achieving grade changes when changes did occur, they were slightly more likely to increase for female students.
 Statistically, this 3% difference in outcomes, does not explain a great deal regarding the skewed gender implications but further research is required to understand the broader implications.
+
+```{r}
+#| label: fig-RegreadeResultsByInstGenderFinal
+#| fig-cap: Instructor Survey End of Semester Regrade Results by Gender of Students and Gender of Instructor
+#| fig-subcap: ["Panel A.  End of Semester Grades, Male Instructors", "Panel B. End of Semester Grades, Female Instructors"]
+#| layout-ncol: 1
+#| warning: false
+#| message: false
+#| echo: false
+
+# Based off code from Chat GPT 3.5 
+# PANEL A: During Semester Grades, Male Instructors Bar Graph
+
+# Gathering Data of End of Semester Grades for Male and Female Students who had a Male Instructor
+male_inst_dta <- inst_data_cleaned |>
+  filter(inst_gender == "Male")
+
+# Male Students
+maleup_avg_maleInst <- mean(male_inst_dta$maleup_fn, na.rm = TRUE)
+malesame_avg_maleInst <- mean(male_inst_dta$malesame_fn, na.rm = TRUE)
+maledown_avg_maleInst <- mean(male_inst_dta$maledown_fn, na.rm = TRUE)
+
+# Female Students
+femaleup_avg_maleInst <- mean(male_inst_dta$femaleup_fn, na.rm = TRUE)
+femalesame_avg_maleInst <- mean(male_inst_dta$femalesame_fn, na.rm = TRUE)
+femaledown_avg_maleInst <- mean(male_inst_dta$femaledown_fn, na.rm = TRUE)
+
+# Create a data frame with the results
+inst_results_male <- data.frame(
+  value = c(maleup_avg_maleInst, femaleup_avg_maleInst, malesame_avg_maleInst, femalesame_avg_maleInst, maledown_avg_maleInst, femaledown_avg_maleInst),
+  category = rep(c("Grade Increase", "No Change", "Grade Decrease"), each = 2),
+  student = rep(c("Male", "Female"), times = 3)
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'Category' variable to a factor with the specified order
+inst_results_male$category <- factor(inst_results_male$category, levels = category_order)
+
+# Create a dodged bar graph using ggplot with position_dodge2
+ggplot(inst_results_male, aes(x = category, y = value, fill = student)) +
+  geom_bar(stat = "identity", position = position_dodge2(width = 0.9), width = 0.7) +
+  geom_text(aes(label = round(value)), position = position_dodge2(width = 0.9), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(x = "Category",
+       y = "Percent", 
+       fill = "Student Gender") +
+  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +  # Adjust colors
+  theme_minimal()
+
+# PANEL B: During Semester Grades, Female Instructors Bar Graph
+
+# Gathering Data of End of Semester Grades for Male and Female Students who had a Female Instructor
+male_inst_dta <- inst_data_cleaned |>
+  filter(inst_gender == "Female")
+
+# Male Students
+maleup_avg_maleInst <- mean(male_inst_dta$maleup_fn, na.rm = TRUE)
+malesame_avg_maleInst <- mean(male_inst_dta$malesame_fn, na.rm = TRUE)
+maledown_avg_maleInst <- mean(male_inst_dta$maledown_fn, na.rm = TRUE)
+
+# Female Students
+femaleup_avg_maleInst <- mean(male_inst_dta$femaleup_fn, na.rm = TRUE)
+femalesame_avg_maleInst <- mean(male_inst_dta$femalesame_fn, na.rm = TRUE)
+femaledown_avg_maleInst <- mean(male_inst_dta$femaledown_fn, na.rm = TRUE)
+
+# Create a data frame with the results
+inst_results_male <- data.frame(
+  value = c(maleup_avg_maleInst, femaleup_avg_maleInst, malesame_avg_maleInst, femalesame_avg_maleInst, maledown_avg_maleInst, femaledown_avg_maleInst),
+  category = rep(c("Grade Increase", "No Change", "Grade Decrease"), each = 2),
+  student = rep(c("Male", "Female"), times = 3)
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'Category' variable to a factor with the specified order
+inst_results_male$category <- factor(inst_results_male$category, levels = category_order)
+
+# Create a dodged bar graph using ggplot with position_dodge2
+ggplot(inst_results_male, aes(x = category, y = value, fill = student)) +
+  geom_bar(stat = "identity", position = position_dodge2(width = 0.9), width = 0.7) +
+  geom_text(aes(label = round(value)), position = position_dodge2(width = 0.9), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(x = "Category",
+       y = "Percent", 
+       fill = "Student Gender") +
+  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +  # Adjust colors
+  theme_minimal()
+
+```
+
+```{r}
+#| label: fig-RegreadeResultsByInstGenderDuring
+#| fig-cap: Instructor Survey During Semester Regrade Results by Gender of Students and Gender of Instructor
+#| fig-subcap: ["Panel A.  During Semester Grades, Male Instructors", "Panel B. During Semester Grades, Female Instructors"]
+#| layout-ncol: 1
+#| warning: false
+#| message: false
+#| echo: false
+
+# Based off code from Chat GPT 3.5
+
+# PANEL A: During Semester Grades, Male Instructors Bar Graph
+
+# Gathering Data of During Semester Grades for Male and Female Students who had a Male Instructor
+male_inst_dta <- inst_data_cleaned |>
+  filter(inst_gender == "Male") # finding results for students who had a MALE instructor
+
+# Male Students 
+maleup_avg_maleInst <- mean(male_inst_dta$maleup_mt, na.rm = TRUE)
+malesame_avg_maleInst <- mean(male_inst_dta$malesame_mt, na.rm = TRUE)
+maledown_avg_maleInst <- mean(male_inst_dta$maledown_mt, na.rm = TRUE)
+
+# Female Students
+femaleup_avg_maleInst <- mean(male_inst_dta$femaleup_mt, na.rm = TRUE)
+femalesame_avg_maleInst <- mean(male_inst_dta$femalesame_mt, na.rm = TRUE)
+femaledown_avg_maleInst <- mean(male_inst_dta$femaledown_mt, na.rm = TRUE)
+
+# Create a data frame with the results
+inst_results_male <- data.frame(
+  value = c(maleup_avg_maleInst, femaleup_avg_maleInst, malesame_avg_maleInst, femalesame_avg_maleInst, maledown_avg_maleInst, femaledown_avg_maleInst),
+  category = rep(c("Grade Increase", "No Change", "Grade Decrease"), each = 2),
+  student = rep(c("Male", "Female"), times = 3)
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'Category' variable to a factor with the specified order
+inst_results_male$category <- factor(inst_results_male$category, levels = category_order)
+
+# Create a dodged bar graph using ggplot with position_dodge2
+ggplot(inst_results_male, aes(x = category, y = value, fill = student)) +
+  geom_bar(stat = "identity", position = position_dodge2(width = 0.9), width = 0.7) +
+  geom_text(aes(label = round(value)), position = position_dodge2(width = 0.9), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(x = "Category",
+       y = "Percent", 
+       fill = "Student Gender") +
+  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +  # Adjust colors
+  theme_minimal()
+
+# PANEL B: During Semester Grades, Female Instructors Bar Graph
+
+# Gathering Data of During Semester Grades for Male and Female Students who had a Female Instructor
+male_inst_dta <- inst_data_cleaned |>
+  filter(inst_gender == "Female") # finding results for students who had a FEMALE instructor
+
+# Male Students
+maleup_avg_maleInst <- mean(male_inst_dta$maleup_mt, na.rm = TRUE)
+malesame_avg_maleInst <- mean(male_inst_dta$malesame_mt, na.rm = TRUE)
+maledown_avg_maleInst <- mean(male_inst_dta$maledown_mt, na.rm = TRUE)
+
+# Female Students
+femaleup_avg_maleInst <- mean(male_inst_dta$femaleup_mt, na.rm = TRUE)
+femalesame_avg_maleInst <- mean(male_inst_dta$femalesame_mt, na.rm = TRUE)
+femaledown_avg_maleInst <- mean(male_inst_dta$femaledown_mt, na.rm = TRUE)
+
+# Create a data frame with the results
+inst_results_male <- data.frame(
+  value = c(maleup_avg_maleInst, femaleup_avg_maleInst, malesame_avg_maleInst, femalesame_avg_maleInst, maledown_avg_maleInst, femaledown_avg_maleInst),
+  category = rep(c("Grade Increase", "No Change", "Grade Decrease"), each = 2),
+  student = rep(c("Male", "Female"), times = 3)
+)
+
+# Define the desired order of categories
+category_order <- c("Grade Decrease", "No Change", "Grade Increase")
+
+# Convert the 'Category' variable to a factor with the specified order
+inst_results_male$category <- factor(inst_results_male$category, levels = category_order)
+
+# Create a dodged bar graph using ggplot with position_dodge2
+ggplot(inst_results_male, aes(x = category, y = value, fill = student)) +
+  geom_bar(stat = "identity", position = position_dodge2(width = 0.9), width = 0.7) +
+  geom_text(aes(label = round(value)), position = position_dodge2(width = 0.9), vjust = -0.5, size = 3) +  # Add labels on top of bars
+  labs(x = "Category",
+       y = "Percent", 
+       fill = "Student Gender") +
+  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +  # Adjust colors
+  theme_minimal()
+
+```
+
+However, there appears to be a different trend, looking at @fig-RegreadeResultsByInstGenderFinal and @fig-RegreadeResultsByInstGenderDuring.
+These graphs provide the average percentage of students’ regrade outcomes by the gender of the instructors.
+In particular, for both male and female instructors, during the semester or at the end of the semester, female students are more likely to receive a grade increase if they do ask for regrades, at respectively 39% and 20% (male instructors) and 35% and 21% (female instructors).
+When coupled with data on the distribution of grade increase by instructors’ gender too, the dataset also reveals a similar trend.
+From @fig-RegreadeResultsByTimeGenderLine, when marked by male instructors, male students are more likely to receive a 0-10% grade increase compared to their female counterparts, whose grades increased by 12.5-25%.
+As for regrades during the semester, male and female students give out similarly favourable grade increases.
+However, female instructors are slightly more likely to give higher grade increases to female students compared to male students.
+We had assumed that male students would have favourable increases from both male and female instructors.
+However, with this new insight from analyzing regrades and instructor’s gender identity, we see that both female and male instructors give out more grade increases upon regrading to female students compared to male students.
+This could be attributed to the new social norm to ‘lift’ up these students to promote a more equal playing field.
+
+```{r}
+#| label: fig-RegreadeResultsByTimeGenderLine
+#| fig-cap: Instructor Survey Regrade Results by Timing, Students’ Gender and Gender of Instructor
+#| fig-subcap: [Panel A. End of Semester Regrade Increase, Panel B. During Semester Regrade Increase]
+#| layout-ncol: 2
+#| warning: false
+#| message: false
+#| echo: false
+
+# PANEL A: End of Semester Regrade Increase Graph 
+inst_data_cleaned |>
+  group_by(maleup_fn, femaleup_fn, inst_gender) |> # grouping by male and female whose final grade increased 
+  count() |>
+  ggplot(aes(x=femaleup_fn, y= maleup_fn, color=inst_gender)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) +
+  labs(title="Male & Female Regrade Increase By Instructor, End of Semester", x="Female Student Grade Increase Percentage", y="Male Student Grade Increase Percentage", color= "Instructor Gender") +
+  scale_color_manual(values=c("#A83B48","#4B659D"), labels=c("Female","Male")) +
+  theme_minimal()
+
+# PANEL B: During Semester Regrade Increase 
+inst_data_cleaned |>
+  group_by(maleup_mt, femaleup_mt, inst_gender) |> # grouping by male and female students whose grade increased during semester
+  count() |>
+  ggplot(aes(x=femaleup_mt, y= maleup_mt, color=inst_gender)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) +
+  labs(title="Male & Female Regrade Increase By Instructor, During Semester", x="Female Student Grade Increase Percentage", y="Male Student Grade Increase Percentage",  color= "Instructor Gender") +
+  scale_color_manual(values=c("#A83B48","#4B659D"), labels=c("Female","Male")) +
+  theme_minimal()
+
+```
+
+@fig-RegreadeResultsByTimeGenderLine also projects that, compared to regrades during the semester, instructors are more likely to provide favourable grade increases for regrades at the end of the semester.
+This trend of grade increase at the end of the semester could be attributed to the notion that at the end of the semester, instructors can see student progress throughout the course thus adjusting in areas upon requests made.
+Male instructors, in particular, are more likely to give out a substantial grade increase (by 50-100%) compared to female instructors.
+While female instructors do give favourable grade increases, this occurs more often in the 0-50% increase range.
 
@@
 To note, there are further pain points regarding the gendered nature of the dataset, making the analysis reductive.
-Previous research has remarked on the discrimination against people of sexual minority background in educational settings (LGBTQI+), which poses considerable alarm on how they would be unfavourable when it comes to regrade requests in a college setting as well [@WilliamsInstitute].
-However, the study only assesses regrade requests from a binary, gendered perspective since the participants identified as either males or females.
-This thus limits the study’s assessment of those who identify as non-binary, two-spirited or gender-fluid.
+Previous research has remarked on the discrimination against people of sexual minority background in educational settings (LGBTQI+), which poses considerable alarm on how they would be unfavourable when it comes to regrade requests in a college setting [@WilliamsInstitute].
+However, the study only assesses regrade requests from a binary gendered perspective since the participants identified as either males or females.
+This limits the study’s assessment of those who identify as non-binary, two-spirited or gender-fluid.
 Accordingly, we recognize that simplifying the gender spectrum to a mere binary of males and females can disregard the struggles non-binary people have against college discrimination (or re-grading in this paper’s context).
 Contextually, the original study simulates a classroom setting within a closed laboratory to survey the implications of regrade requests.
-The study thus requires participants to perform their student identity and imitate their regrade request scenarios, which could have posited the students to have a ‘formal”, heteronormative identity to fit in with the study’s nature.
-This method thus could have influenced student behaviours.
+The study required participants to perform their student identity and imitate their regrade request scenarios, which could have posited the students to have a ‘formal”, heteronormative identity to fit in with the study’s nature, modifying their overall behaviour.
 It drives students away from a typical scenario of regrade requests, where there is a big power difference between a student and an actual professor.
-This, in many ways, denaturalized the nature of regrade requests and affected the study’s results.
 
@@
 
-Since this paper was a replication, our analysis was limited to results and interpretations made by Li and Zahar from the original paper.
-We decided to focus on one aspect of the paper rather than having the time to explore the other possible relationships with the data.
-If we had additional time and resources we would have liked to see the other findings within Li and Zahar’s paper regarding payments and regarding requests in the lab and how those data sets relate to ours.
-If we had additional time and resources, we would have expanded our investigation to include other findings from Li and Zahar's paper, particularly those related to the positive social costs of regrade requests and lab requirements.
-These additional insights could provide a more comprehensive understanding of the dynamics surrounding grade regrade requests among college students.
-By incorporating these findings, we could further elucidate the factors influencing students' behaviours and outcomes in academic settings, contributing to a richer and more nuanced analysis of gender disparities within academia.
+Since this paper was based on another paper, our analysis was limited to the results and interpretations made by Li and Zahar’s original findings.
+We decided to focus mainly on one aspect of the paper–instructor’s gender and favorable regrade requests–rather than exploring the other possible relationships within the data.
+If we had additional time and resources we would have liked to extrapolate on the other findings within Li and Zahar’s paper, regarding positive costs of regrade requests and the personality of students associated with simulating regrade requests in the lab.
+These additional insights could provide a more comprehensive understanding of the dynamics surrounding regrade requests among college students.
+By incorporating these findings, we could further clarify the factors influencing students' behaviours and outcomes in academic settings, contributing to a richer and more nuanced analysis of gender disparities within academia.
 
@@
 We are not sure why the results are different as the same dataset from the original graph was used to replicate.
-We assume the cause for this distortion can be attributed to the different logic used in R rather than Stata.
+We assume the cause for this distortion can be attributed to the different logic used in R rather than Stata as used by the original authors.
 

### 2024-02-20 scripts/00-simulate_data.R

@@ -2,7 +2,7 @@
 # Purpose: Simulates dataset of correlation between gender identities and regrades among undergraduate students, 2010-2016 
 # Author: Quang Mai, Catherine Punnoose and Faiza Imam
 # Date: 12 February 2024 
-# Contact:
+# Contact: catherine.punnoose@mail.utoronto.ca, q.mai@mail.utoronto.ca, faiza.imam@mail.utoronto.ca
 # License: MIT
 
 

### 2024-02-20 scripts/01-download_data.R

@@ -2,7 +2,7 @@
 # Purpose: Downloads and saves survey data to new file
 # Author: Faiza Imam, Catherine Punnoose, Quang Mai 
 # Data: survey.dta
-# Contact: 
+# Contact: catherine.punnoose@mail.utoronto.ca, q.mai@mail.utoronto.ca, faiza.imam@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Have downloaded survey.dta from https://doi.org/10.7910/DVN/QXJDJ5
 

### 2024-02-20 scripts/02-data_cleaning.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
+# Purpose: Cleans the data collected from the article ‘Ask and You Shall Receive? Gender differences in Regrades in College’
 # Author: Catherine Punnoose, Quang Mai, Faiza Imam 
 # Date: 13 Feb 2024 
-# Contact: catherine.punnoose@mail.utoronto.ca
+# Contact: catherine.punnoose@mail.utoronto.ca, q.mai@mail.utoronto.ca, faiza.imam@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 01-download_data.R
 
 #### Workspace setup ####
 library(dplyr)
@@ -21,7 +20,11 @@ inst_data <- read.csv("inputs/data/instsurvey.csv")
 inst_data_cleaned <- 
   inst_data |>
   janitor::clean_names() |>
-  select(id, maleup_fn, femaleup_fn, malesame_fn, femalesame_fn, maledown_fn, femaledown_fn, maleup_mt, femaleup_mt, malesame_mt, femalesame_mt, maledown_mt, femaledown_mt) |>
+  select(id, maleup_fn, femaleup_fn, malesame_fn, femalesame_fn, maledown_fn, femaledown_fn, maleup_mt, femaleup_mt, malesame_mt, femalesame_mt, maledown_mt, femaledown_mt, inst_female) |>
+  mutate(inst_gender = case_match(inst_female, 
+                                0 ~ "Male",
+                                1 ~ "Female")) |>
+  select(-inst_female) |>
   tidyr::drop_na()
 
 #### Save Clean Instsurvey data ####

### 2024-02-20 scripts/03-test_data.R

@@ -3,7 +3,7 @@
 # Purpose: Tests cleaned datasets 
 # Author: Quang Mai, Catherine Punnoose and Faiza Imam
 # Date: 11 February 2024
-# Contact:
+# Contact: catherine.punnoose@mail.utoronto.ca, q.mai@mail.utoronto.ca, faiza.imam@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: reload 01-download_data.R and 02-data_cleaning.R
 

### 2024-02-20 outputs/paper/paper.qmd
finalize paper

@@
 date-format: long
-abstract: "Academia often exacerbates gender differences.
-This paper further explores the gender implications behind regrade requests of undergraduate students at Colorado State University from 2010-2016.
-By analyzing changes in regrade request patterns throughout the semester, actual grade changes, and instructor’s gender identity, our results show that on average male students are more likely to submit regrade requests, and are more likely–even when they request regrade for more courses–to have better grade changes compared to female students.
-In addition, extrapolation on the original study seems to suggest that both female and male instructors are more likely to give out favourable regrades for female students, which raises interesting questions on gender dynamics and regrading in the college setting."
+abstract: "Academia often aggravates gender differences.
+This paper then aims to explore the gendered nature of regrade requests by undergraduate students at Colorado State University from 2010-2016.
+Through analyzing changes in regrade request patterns, regrade outcomes, and instructors’ gender identity, our results show that on average male students are more likely to submit regrade requests, and are more likely to have better grade changes compared to female students.
+In contrast, extrapolation on the original study suggests that both female and male instructors are more likely to favourably regrade female students, which raises interesting questions on gender dynamics in the college setting."
 format: pdf
@@
 # Load data
-inst_data <- read.csv(here::here("inputs/data/inst_data_cleaned.csv"))
-std_data <- read_csv(here::here("inputs/data/stdsurvey.csv"))
-inst_data_cleaned <- read_csv(here::here("inputs/data/inst_data_cleaned.csv"))
+inst_data <- read.csv(here::here("inputs/data/raw data/instsurvey.csv"))
+std_data <- read_csv(here::here("inputs/data/raw data/stdsurvey.csv"))
+inst_data_cleaned <- read_csv(here::here("inputs/data/cleaned data/inst_data_cleaned.csv"))
 ```
@@
 
-It’s a societal norm that we consider men to be assertive and dominant in leadership roles while women are nurturing and supportive.
-Often, women who choose to break out of these stereotypes and speak out against misogyny and sexism are labelled ‘emotional’ or ‘aggressive’, hindering their professional mobility [@AACSB].
+It’s a social norm that we consider men to be assertive and dominant, while women nurturing and supportive.
+Often, women who choose to break out of these stereotypes are labelled ‘emotional’ or ‘aggressive’, hindering their professional mobility [@AACSB].
 Even in academic settings, women tend to be penalized when achieving better grades and opportunities.
@@
 
-This begs whether these unequal tendencies exist in higher education for women, as they attempt to have their academic achievements recognized by requesting regrades.
-There are many reasons to account for when analyzing gendered inequality.
-First, being subjected to societal norms, women tend to be more non-confrontational, resulting in them accepting their academic results as they are instead of fighting for them [@AACSB].
+As such, whether or not these unequal tendencies exist in higher education for women-especially in the context of requesting regrade-is an important question to ask.
+There is already much research attempted to answer this problem space.
+First, being subjected to social norms, women tend to be more non-confrontational, resulting in them accepting their academic results as they are instead of fighting for them [@AACSB].
 Second, with differing confidence levels and personalities, women tend to second-guess their abilities, hence preventing them from requesting aid from their institutions as they see the entire process as ‘tedious’ and “unnecessary’ [@SageJournals].
-Lastly, fear of rejection, women tend to harbour higher levels of stress and embarrassment when considering regrade requests as they assume that the result will often be a rejection from their instructors [@SageJournals].
-A paper published by the American Journal of Political Science by Li and Zahar delves into the differences that arise between genders when requesting grade changes among college students from Colorado State University from 2010 to 2018.
-According to their findings, male students are more likely to request grade changes than their female counterparts, accounting for 18.6% higher of receiving a favourable grade change.
-Regardless of the class number, males are more likely to ask for grade changes throughout the semester [@InsideHigherEd].
-Overall there is a gender disparity among college students regarding regrade requests.
-Hence, by examining biases inherent within higher education, the paper contributes to understanding the power dynamics between two gender demographics.
-In addition, to extrapolate from the original paper, our paper combines the student regrade data with instructors’ gender to see if there is gender dynamics between the two.
+Lastly, fear of rejection and being viewed negatively by instructors, women tend to harbor higher levels of stress when considering regrades [@SageJournals].
+A paper published by the American Journal of Political Science by Li and Zahar focuses into the gendered differences in regrade outcomes among college students from Colorado State University from 2010 to 2016.
+According to their findings, male students are more likely to request grade changes than their female counterparts.
+Regardless of the class number as well, males are more likely to ask for regrades throughout the semester [@InsideHigherEd].
+Overall, there is a gender disparity among college students regarding regrade requests.
 
-Thus, from the paper, ‘Ask and You Shall Receive?
-Gender differences in Regrades in College’ by Li and Zafar, we hope to look into the estimand that upon a regrade request, whether or not an instructor’s gender identity–when interacted with a student’s gender identity– affects the outcome of such a student’s re-grading.
-Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings?’, ‘Are there fluctuations in regrade request patterns among male and female students regarding their class number?’ and ‘Is there a correlation between instructor's gender and the regrading process?’
+Then, while the paper, ‘Ask and You Shall Receive?
+Gender differences in Regrades in College’ by Li and Zafar focuses on students' gender and regrades, we moreso look into the estimand that, upon a regrade request, whether or not an instructor’s gender identity–when interacted with a student’s gender identity–affects the regrade outcome.
+Our study attempts to answer this question, ‘Is there a correlation between instructor's gender and the regrading process?’ Hence, by examining biases inherent within higher education, the paper aims to assess the relationship between regrade requests and gender identity, especially the complex dynamics between instructors' and students' gender identity.
 
@@
 
-Published by the ‘American Economic Journal: Economic Policy’, this paper reproduced the paper ‘Ask and You Shall Receive?
+This paper reproduced the paper ‘Ask and You Shall Receive?
 Gender Differences in Regrades in College’ and its replication package published on `openICPSR` [@openICPSR].
@@
 
-Further, to analyze the differences in favourable regrades between male and female instructors, we renamed the original variable, “inst_female”  into “inst_gender”.
+Further, to analyze the differences in favorable regrades amng male and female instructors, we renamed the original variable, “inst_female”  into “inst_gender”.
 We also changed “0” into “Male” and “1” into “Female to clarify the dataset.
-After that, we attempt to create four bar graphs to assess the correlation between instructors’ gender identity and favourable grade increases.
+After that, we attempt to create four bar graphs and two scatter-plots to assess the correlation between instructors’ gender and favorable regrades.
 
@@
 #| label: fig-RegreadeResultsByTime
-#| fig-cap: Instructor Survey Regrade Results by Timing and Students’ Gender
-#| fig-subcap: [Panel A. End of semester male students, Panel B. End of semester female students, Panel C. During semester male students, Panel D. During semester female students]
+#| fig-cap: Regrade Results by Timing and Students’ Gender
+#| fig-subcap: [End of semester male students, End of semester female students, During semester male students, During semester female students]
 #| layout-ncol: 2
@@
 #| label: fig-RegradeByClass
-#| fig-cap: Student Survey Number of Classes Students Considered for Regrade Requests by Students’ Gender
+#| fig-cap: Number of Classes Students Considered for Regrade Requests by Students’ Gender
 #| warning: false
@@
 
-One key point to consider is the disparity in outcomes between male and female students when requesting a regrade.
+Within @fig-RegreadeResultsByTime, one key point to consider is the disparity in outcomes between male and female students when requesting a regrade.
 The data shows that a higher percentage of male students (62%) received no change in their grade after requesting a regrade during the semester compared to female students (59%).
@@
 #| label: fig-RegreadeResultsByInstGenderFinal
-#| fig-cap: Instructor Survey End of Semester Regrade Results by Gender of Students and Gender of Instructor
-#| fig-subcap: ["Panel A.  End of Semester Grades, Male Instructors", "Panel B. End of Semester Grades, Female Instructors"]
-#| layout-ncol: 1
+#| fig-cap: End of Semester Regrade Results by Student and Instructor Gender
+#| fig-subcap: ["End of Semester Grades, Male Instructors", "End of Semester Grades, Female Instructors"]
+#| layout-ncol: 2
 #| warning: false
@@
 #| label: fig-RegreadeResultsByInstGenderDuring
-#| fig-cap: Instructor Survey During Semester Regrade Results by Gender of Students and Gender of Instructor
-#| fig-subcap: ["Panel A.  During Semester Grades, Male Instructors", "Panel B. During Semester Grades, Female Instructors"]
-#| layout-ncol: 1
+#| fig-cap: During Semester Regrade Results by Student and Instructor Gender
+#| fig-subcap: ["During Semester Grades, Male Instructors", "During Semester Grades, Female Instructors"]
+#| layout-ncol: 2
 #| warning: false
@@
 When coupled with data on the distribution of grade increase by instructors’ gender too, the dataset also reveals a similar trend.
-From @fig-RegreadeResultsByTimeGenderLine, when marked by male instructors, male students are more likely to receive a 0-10% grade increase compared to their female counterparts, whose grades increased by 12.5-25%.
-As for regrades during the semester, male and female students give out similarly favourable grade increases.
-However, female instructors are slightly more likely to give higher grade increases to female students compared to male students.
+From @fig-RegreadeResultsByTimeGenderLine, when marked by male instructors, male students are more likely to receive a 0-10% grade increase compared to their female counterparts, whose grades increased by 12.5-25%, observable in the blue clusters in the bottom left of both graphs and how they are more skewed towards the x-axis.
+As for regrades during the semester, male and female students give out similarly favourable grade increases due to the similar correlation lines.
+However, female instructors are slightly more likely to give higher grade increases to female students compared to male students, as observed in the red correlation line being more skewed towards the x-axis.
 We had assumed that male students would have favourable increases from both male and female instructors.
@@
 #| label: fig-RegreadeResultsByTimeGenderLine
-#| fig-cap: Instructor Survey Regrade Results by Timing, Students’ Gender and Gender of Instructor
-#| fig-subcap: [Panel A. End of Semester Regrade Increase, Panel B. During Semester Regrade Increase]
+#| fig-cap: Regrade Results by Timing, Students’ Gender and Gender of Instructor
+#| fig-subcap: [Regrade Increase End of Semester, Regrade Increase During Semester]
 #| layout-ncol: 2
@@
   geom_smooth(method="lm", se=FALSE) +
-  labs(title="Male & Female Regrade Increase By Instructor, End of Semester", x="Female Student Grade Increase Percentage", y="Male Student Grade Increase Percentage", color= "Instructor Gender") +
+  labs(x="Female Student Grade Increase Percentage", y="Male Student Grade Increase Percentage", color= "Instructor Gender") +
   scale_color_manual(values=c("#A83B48","#4B659D"), labels=c("Female","Male")) +
@@
   geom_smooth(method="lm", se=FALSE) +
-  labs(title="Male & Female Regrade Increase By Instructor, During Semester", x="Female Student Grade Increase Percentage", y="Male Student Grade Increase Percentage",  color= "Instructor Gender") +
+  labs(x="Female Student Grade Increase Percentage", y="Male Student Grade Increase Percentage",  color= "Instructor Gender") +
   scale_color_manual(values=c("#A83B48","#4B659D"), labels=c("Female","Male")) +
@@
 
-@fig-RegreadeResultsByTimeGenderLine also projects that, compared to regrades during the semester, instructors are more likely to provide favourable grade increases for regrades at the end of the semester.
-This trend of grade increase at the end of the semester could be attributed to the notion that at the end of the semester, instructors can see student progress throughout the course thus adjusting in areas upon requests made.
-Male instructors, in particular, are more likely to give out a substantial grade increase (by 50-100%) compared to female instructors.
-While female instructors do give favourable grade increases, this occurs more often in the 0-50% increase range.
+@fig-RegreadeResultsByTimeGenderLine also projects that, compared to regrades at the end of the semester, instructors are more likely to provide favorable grade increases for regrades during the semester, as seen in the consistent grade increase of both male and female students in the second scatter-plot.
+This trend of grade increase during the semester could be attributed to the notion that  during the semester, the grades' weight are less impactful throughout the course thus making grade adjustment easier.
+Male instructors, in particular, are more likely to give out consistent and substantial grade increases (by 50-100%) to both male and female students compared to female instructors, as observed in the blue clusters on the top right of each graph and how they are closely aligned with the correlation lines.
+While female instructors do give favorable grade increases, this occurs more often in the 0-50% increase range and more inconsistently, observable in the red clusters in the bottom left of both graphs and how they are more scattered.
 
-## Trends Among Female Students and Course Load
+## Trends Among Student Gender and Regrade Requests for Different Number of Classes
 
-Another trend suggests that regrade consideration between male and female students is attributed to the number of courses they are taking.
-Female students are more inclined to submit regrade requests when taking fewer courses as 30.4% consider a regrade request when taking one course, while male students consideration is around 22.7%.
+Another trend from @fig-RegradeByClass suggests that regrade consideration between male and female students depends on the number of classes that they have.
+Female students are more inclined to submit regrade requests when taking fewer courses as 30.4% consider a regrade request when taking one course, compared to 22.7% of male students.
 However, when the course load is higher the trend is reversed.
@@
 Vice versa, females on average are only likely to ask for regrade in one class even if they have more than one class that necessitates regrade consideration.
-This trend could be attributed to the notion that with 1 course, more investment is required hence the motivation to work harder.
-Compared to a higher course load which requires time management and balance.
+This trend could be attributed to the notion that with 1 course, more investment is required hence the motivation to work harder.Compared to a higher course load which requires time management and balance.
 

### 2024-02-20 scripts/01-download_data.R

@@ -11,12 +11,9 @@ library(readstata13)
 library(readr)
 
 #reading in the stata file
-instsurvey <- read.dta13(here::here("inputs/data/instsurvey.dta"))
-stdsurvey <- read.dta13(here::here("inputs/data/stdsurvey.dta"))
-experiment <- read.dta13(here::here("inputs/data/experiment.dta"))
-
+instsurvey <- read.dta13(here::here("inputs/data/raw data/instsurvey.dta"))
+stdsurvey <- read.dta13(here::here("inputs/data/raw data/stdsurvey.dta"))
 
 #writing to csv
-write_csv(instsurvey, here::here("inputs/data/instsurvey.csv"))
-write_csv(stdsurvey, here::here("inputs/data/stdsurvey.csv"))
-write_csv(experiment, here::here("inputs/data/experiment.csv"))
+write_csv(instsurvey, here::here("inputs/data/raw data/instsurvey.csv"))
+write_csv(stdsurvey, here::here("inputs/data/raw data/stdsurvey.csv"))

### 2024-02-20 scripts/02-data_cleaning.R

@@ -19,7 +19,7 @@ library(tidyverse)
 ### CLEANING DATA ###
 ### Cleaning Instructor	Survey	Data (instsurvey) ###
 # Read data
-inst_data <- read.csv("inputs/data/instsurvey.csv")
+inst_data <- read.csv("inputs/data/raw data/instsurvey.csv")
 
 inst_data_cleaned <- 
   inst_data |>
@@ -32,10 +32,10 @@ inst_data_cleaned <-
   tidyr::drop_na()
 
 #### Save Clean Instsurvey data ####
-write_csv(inst_data_cleaned, "inputs/data/inst_data_cleaned.csv")
+write_csv(inst_data_cleaned, "inputs/data/cleaned data/inst_data_cleaned.csv")
 
 ### Cleaning Stdsurvey ###
-std_data <- read.csv("inputs/data/stdsurvey.csv")
+std_data <- read.csv("inputs/data/raw data/stdsurvey.csv")
 
 std_data_cleaned <- 
   std_data |>
@@ -43,6 +43,4 @@ std_data_cleaned <-
   select(participantcode, std_female, std_standing, std_male, consider_regrade, everasked, num_class, num_asked)
 
 #### Save Clean Stdsurvey data ####
-write_csv(std_data_cleaned, "inputs/data/std_data_cleaned.csv")
-
-
+write_csv(std_data_cleaned, "inputs/data/cleaned data/std_data_cleaned.csv")

### 2024-02-20 scripts/03-test_data.R

@@ -16,16 +16,11 @@ library(janitor)
 #### Read in cleaned data ####
 
 # read cleaned data on arrests and strip searches
-std_data_cleaned = read_csv(
-  file = here("inputs/data/std_data_cleaned.csv"),
-  show_col_types = FALSE
-)
+std_data_cleaned <- read.csv("inputs/data/cleaned data/std_data_cleaned.csv")
+
 
 # read cleaned data on race and gender and strip searches
-inst_data_cleaned = read_csv(
-  file = here("inputs/data/inst_data_cleaned.csv"),
-  show_col_types = FALSE
-)
+inst_data_cleaned <- read.csv("inputs/data/cleaned data/inst_data_cleaned.csv")
 
 
 #### Test data ####
@@ -58,8 +53,8 @@ std_data_cleaned$std_male |> unique() |> length() == 2
 
 
 
-# Test 6: check that there are 127 observations in the inst_data_cleaned dataset
-inst_data_cleaned$id |> unique() |> length() == 127
+# Test 6: check that there are 115 observations in the inst_data_cleaned dataset
+inst_data_cleaned$id |> unique() |> length() == 115
 
 
 # Test 7: check that there are maximum 100 maleup/femaleup and 0 minimum maleup/femaleup in inst_data_cleaned
@@ -73,6 +68,10 @@ inst_data_cleaned$femaleup_fn  |> max() == 100
 # Test 8: check that there are minimum malesame/femalesame in inst_data_cleaned
 inst_data_cleaned$malesame_fn |> min() == 0
 inst_data_cleaned$femalesame_fn |> min() == 0
+
+# Test 9: check that there are  2 genders in inst_data_cleaned
+inst_data_cleaned$inst_gender |> unique() |> length() == 2
+
 
 
 

### 2024-02-20 scripts/02-data_cleaning.R
finalize paper

@@ -1,9 +1,6 @@
 #### Preamble ####
-<<<<<<< HEAD
 # Purpose: Cleans the data collected from the article ‘Ask and You Shall Receive? Gender differences in Regrades in College’
-=======
-# Purpose: Clean up the survey.dta from https://doi.org/10.7910/DVN/QXJDJ5. Specifically selecting columns participantcode, std_female, std_standing, std_male, consider_regrade, everasked, num_class, num_asked).
->>>>>>> 3d9be9f6bb0cc6db6eb351c33fca37c617e7c9c0
+# Purpose: Clean up the survey.dta from https://doi.org/10.7910/DVN/QXJDJ5.
 # Author: Catherine Punnoose, Quang Mai, Faiza Imam 
 # Date: 13 Feb 2024 
 # Contact: catherine.punnoose@mail.utoronto.ca, q.mai@mail.utoronto.ca, faiza.imam@mail.utoronto.ca
